---
title: "6_Report"
author: "Arturo Bertero"
date: "2026-03-03"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 6
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  message = FALSE, 
  warning = FALSE,
  fig.align = "center",
  out.width = "100%"
)
```

<style>
  /* This forces the browser to remove the massive white space injected by the floating TOC */
  body {
    padding-bottom: 20px !important; 
  }
</style>


```{r}
#clean
rm(list = ls())

library("pacman")
p_load(tidyverse, here, haven, countrycode, sjPlot, lme4, survey, broom,
       marginaleffects, ggeffects, knitr, htmltools)

```

# Basic stuff

[This is the link](https://docs.google.com/document/d/1vXCvlh0D7jgOzoOCICYDhdq45GUHGAXd14CIRQw6hKk/edit?usp=drive_link) to the paper we submitted. 
It is unchanged for now. I draft this report so that we can agree on how to address the critiques.

# Introduction

## Main comments from editor and reviewers

* Causal framing mismatch: We used “CM drives CB” language, but the data are cross-sectional. Must reframe away from causality/dynamics.

* Methods clarity: Need clearer rationale for H1 logic + explanation of node-wise R²; reduce jargon.

* Possible artifact in the key centrality finding: Editor likes the pattern but wants robustness because it might depend on:

    * CB item selection (too “epistemically risky” / not representative; centrality depends on node we selected).

    * Unequal number of items / index vs items (different scale lengths may bias centrality).

    * Skewness of CB items (could inflate correlations/centrality).

    * Alien item in CM (we know it's bad, it might impact on CM measurement).

## The new research design

I adopted a brute force approach. Given we recieved critiques on both our CB and CM scales, 
I was super curious to see if results could be replicated with completely different measures and surveys. 

I restructured the project into a **three-study design** using four independent
operationalizations of CM (4 validated scales widely used in the literature) and many 
different CB items (which vary in their epistemic riskyness).

The general strategy is: 

* Study 1 could be our old paper (but streamlined)
* Replicate the key networks on the *US-based* public data of the notorius [PB paper from Enders et al 2023](https://link.springer.com/article/10.1007/s11109-022-09812-3)
* Replicate the key networks on the *comparative* public data of [this paper](https://link.springer.com/article/10.1057/s41304-023-00463-4)
* We could add a robustness section directly in the Results of the article. Here we could show that: 
    * Skewenness does not matter
    * Number of items in these scales does not matter
    
The two extra study I selected are super nice cause they work with heterogeneous measures: 

| Study        | Dataset / source            | CM measure                          | n CM items | CB measure                       | n CB items |
| ------------ | --------------------------- | ----------------------------------- | ---------: | -------------------------------- | ---------: |
| **Study 1**  | SUSPECTS (original)         | **GCB5**                            |          5 | **COMPCBS** (CB items)           |          8 |
| **Study 2**  | Enders et al. (2023)        | **ACTS**                            |          4 | unvalidated                      |         17 |
| **Study 3a** | Comparative survey          | **CMQ**                             |          5 | unvalidated, differ across country |          4 |
| **Study 3b** | Comparative survey          | **GCB (full)**                      |         14 | unvalidated, differ across country |          4 |

So we play with data in which we have different combos of CM and CB measures. 
Sometimes we have more CB than CM, some other times the reverse. Moreover, we
now feature most of the validated scales of CM. And we even have two kinds of CB
measures: our scale aim at finding a list of cbs that work nice *across* countries; 
all other studies fielded cb that are *country-specific!*

## Hypotheses

Nothing new here.  

1. H0 -> CB and CM load on different factor
2. H1 -> The CM latent variable cancels out the manifest correlations between CB items
3. H2 -> The CB latent variable cancels out the manifest correlations between CM items

### Results

I avoid reporting all the country-network, I just show you the bare 
minimum we need to confirm our 3 hypo. Also, in the paper we can obviously present 
results following the order "study 1 -> 2 -> 3". To save space, here i present results
following the order "H0 -> H1 -> H2".


#### H0 

In all countries we have more evidence for a two factor structure vs a one factor structure. 
But fit is generally mediocre-to-bad for the 2 factor solution. I don't think this will
be particularly problematic, as this is not the key part of our paper. 

This is the table showing fit stats of the two factor models

```{r, results='asis'}
htmltools::includeHTML(here("Output", "H0", "CFA_Fit_Stats_Master.doc"))
```

Despite the fit stats, alphas are super ok!

```{r, results='asis'}
htmltools::includeHTML(here("Output", "H0", "Alpha_Reliability_Master.doc"))
```

This was very important: it means we can apply the old code logic to all new datasets.

#### H1

##### Study 1

In our data, CM was the least central node

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "H1", "H1_Centrality_Study1.pdf"))
```

##### Study 2

The ACTS scale for CM has medium centrality

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "H1", "H1_Centrality_Study2.pdf"))
```


##### Study 3

Here results depend a bit on the scale, but the CM sumscore is never the most central node, 
as it should be under a perfect latent model

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "H1", "H1_Centrality_Study3_CMQ.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "H1", "H1_Centrality_Study3_GCB.pdf"))
```


#### H2

##### Study 1

In our data, CB has medium-to-high centrality

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "H2", "H2_Centrality_Study1.pdf"))
```

##### Study 2

Same here: medium-high

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "H2", "H2_Centrality_Study2.pdf"))
```


##### Study 3

When using the CMQ, the sumscore has the lowest centrality. 

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "H2", "H2_Centrality_Study3_CMQ.pdf"))
```

Circa same results with the GCB-full scale

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "H2", "H2_Centrality_Study3_GCB.pdf"))
```


#### Robustness

Here I try to address the two biggest point: 

1. Items are skewed
2. Scales are un-balanced in terms of number of items

##### Problem 1: CM items are normal, but CB items are left-skewed

Here I go fast, without citing sources. Epskamp has some papers on this issue.

Usually, network models assume **multivariate normality**, which is *not* equal to assume
all items are normally distributed. 

Nevertheless, the two things might be related, and conducting checks on this is quite easy: 

1. I apply a nonparanormal (npn) transformation to all network vars using the huge package
2. I re-estimated all figures I showed you above

Results hold so nicely that these could actually be the main plots of the article!

Below you find the same plot as above, but calculated on the networks fitted with the transformed vars. 

###### H1

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_NPN_H1_Study1.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_NPN_H1_Study2.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_NPN_H1_Study3_CMQ.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_NPN_H1_Study3_GCB.pdf"))
```

###### H2

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_NPN_H2_Study1.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_NPN_H2_Study2.pdf"))
```

```{r, out.width="100%", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_NPN_H2_Study3_CMQ.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_NPN_H2_Study3_GCB.pdf"))
```


##### Problem 2: scales have different number of items

I ll be honest, I'd push back on this critique. 3 reasons: 

1. It is not our fault if scales were validated with different number of items
2. Filtering out some items of a validated scale means working with a completely different scale
3. It is true that the larger the number of items the lower the measurement error; but these are partial corr network, so theoretically items could be isolated in the the network. Hence, I don't see a deterministic relationship between number of items and strength centrality. 

**But this point was also flagged by the editor, so no chance we can ignore it brutally.** 

I explored this option with two routes. 

###### Option 1: just plot mean strength centrality

Here I followed these steps:

* Build country-specific networks with only CM and CB items (NO INDICES)
* For each country × study, run a case-bootstrap (1000 resamples) of the item-level network 
* Extract strength centrality for every node.
* Aggregate within each bootstrap, then compute:
    * Mean_CM: the average strength across all CM items
    * Mean_CB: the average strength across all CB items
* Compare distributions with the usual violins

This asks whether the original CM-CB pattern holds when both constructs are treated symmetrically at the item level (reducing concerns that an index with more items has a mechanical advantage).

Results are quite ok. 

In study 1, the mean centrality of CB items is lower than that of CM items.

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_ItemAvg_Study1.pdf"))
```

Same in study 2!

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_ItemAvg_Study2.pdf"))
```

In study 3 the situation is no results/ or against our argument

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_ItemAvg_Study3_CMQ.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "Robustness_ItemAvg_Study3_GCB.pdf"))
```


###### Option 2: just plot mean strength centrality

Now, the procedure above is a good diagnostic because it removes sumscore/index nodes
entirely and compares CM and CB items vs items. 

However, it does not fully resolve the reviewer’s specific concern that different scale
lengths imply different reliability/error reduction when constructs are represented by aggregated scores.

For this reason, the final test is an equal-item down-sampling Monte Carlo simulation.


For each study × country, the structure is: 

* Identify the set of CM items and CB items.
* Find k, the number of items in the smaller construct (for instance, in SUSPECT data, this number is 5, due to the GCB5).
* Repeat this for 1000 iterations:
    * Fix the smaller construct: include all its items.
    * Downsample the larger construct: randomly select k items from it.
    * Estimate the network on the resulting balanced item set 
    * Compute strength centrality and store summary metrics
    * These metrics are: Δ_mean = mean strength(CB items) − mean strength(CM items); Δ_max: max strength(CB items) − max strength(CM items); CM_top1: whether the most central node is a CM item (tie-handled if needed)
    * Output: per country, we obtain distributions of these metrics across iterations 
    
**I implemented this thing (both code and logic) with Gemini, and checked all with ChatGPT.** 

Tell me if it sounds good to you: it is way outside my comfort zone! And remember, here we focus again on item-level networks. 

I present 3 plots from this simulation. 

Before I give u a **summary of main findings** across all these plots.

1. Study 1: CB items are the most central. 
2. Study 2 (ACTS): CM items are the most central.
3. Study 3: results depend on the scale you use (CMQ is mixed; full GCB tends to be CM-hub).

**TYPE PLOT A**

The first plot shows the distribution of average cb-items strength minus average cm items strength across the 1,000 equal-item iterations.
If violins are above 0: cb items are more central on average; below 0: the reverse.
So this checks overall block centrality: are CB items, on average, more connected than CM items?

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness",  "MC", "MC_PlotA_Mean_Study1.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotA_Mean_Study2.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotA_Mean_Study3_CMQ.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotA_Mean_Study3_GCB.pdf"))
```


**TYPE PLOT B**

The second shows the distribution of the most central cb item minus most central cm item.
If violins are above 0: the network’s top hub is usually a cb item; below 0: usually a cm item.
So this check if is the CM or the CB scale containing the most central item

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotB_Max_Study1.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotB_Max_Study2.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotB_Max_Study3_CMQ.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotB_Max_Study3_GCB.pdf"))
```


**TYPE PLOT C**

The third plot shows, for each country, the probability that a cm item is the single most central node (with Monte Carlo interval bars).
Near 1: a cm item is almost always the central hub; near 0: cm items are almost never the most central; ~0.5: no consistent winner.
This is just a summary of the previous plot. It answers the question: "across the iterations, how often is the single most central node a CM item (rather than a CB item)? 

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotC_Prob_Study1.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotC_Prob_Study2.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotC_Prob_Study3_CMQ.pdf"))
```

```{r, out.width="100%", out.height="1000px", fig.align="center"}
knitr::include_graphics(here("Output", "Robustness", "MC", "MC_PlotC_Prob_Study3_GCB.pdf"))
```


