---
title: "Centrality hypotheses, Connectivity hypotheses"
author: Arturo Bertero
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
date: "2024-12-11"
---

# Input

```{r}
knitr::opts_chunk$set(
  echo = TRUE,
  results = "markup", # Show output
  warning = FALSE,  # Do not show warnings
  message = FALSE   # Do not show messages
)

```

```{r}
#Libraries
library(pacman)
p_load(lavaan, rio, tidyverse, psych, here, stargazer, summarytools, visdat,
       EGAnet, qgraph, ggplot2, haven, janitor, readxl, labelled, reshape2,
       openxlsx, mgm, bootnet)

#Options
rm(list = ls())
options(scipen = 999)
```

```{r}
# Import cleaned data
data = readRDS(here("Input", "Secondary", "data.rds")) 
country_data = readRDS(here("Input", "Secondary", "country_data.rds"))
country_data2 = readRDS(here("Input", "Secondary", "country_data2.rds")) 
country_data3 = readRDS(here("Input", "Secondary", "country_data3.rds")) 
country_data4 = readRDS(here("Input", "Secondary", "country_data4.rds")) 
country_data5 = readRDS(here("Input", "Secondary", "country_data5.rds")) 
country_data6 = readRDS(here("Input", "Secondary", "country_data6.rds")) 
country_data7 = readRDS(here("Input", "Secondary", "country_data7.rds")) 
```

```{r}
#Country_data obj as matrix
country_data <- lapply(country_data, function(sublist) as.matrix(sublist))
country_data2 <- lapply(country_data2, function(sublist) as.matrix(sublist))
country_data3 <- lapply(country_data3, function(sublist) as.matrix(sublist))
country_data4 <- lapply(country_data4, function(sublist) as.matrix(sublist))
country_data5 <- lapply(country_data5, function(sublist) as.matrix(sublist))
country_data6 <- lapply(country_data6, function(sublist) as.matrix(sublist))
country_data7 <- lapply(country_data7, function(sublist) as.matrix(sublist))
```

```{r}
# objects for network 
(shortnames = c("rad_poison","aids_cia","elf_mindcontrol","chemtrails",
              "un_worldgov","rothschild_control","monsanto_gmo","ebola_bigpharma", "GCB"))

# Country color palette 
country_colors <- c(
  "DEU" = "#E41A1C", "ESP" = "#377EB8", "FRA" = "#4DAF4A", 
  "GBR" = "#984EA3", "ITA" = "#FF7F00", "POL" = "#ffcf33", "SWE" = "#A65628"
)

Totalgroup_comm <- list(
  "Conspiracy Beliefs" = c(1:8),
  "Conspiracy Mentality" = c(9))

Totalgroup_cols <- c("#966FD6B3", "#008B8BB3") 

#type
type = c("g","g","g","g","g","g","g","g","g")

#level
level = c(1,1,1,1,1,1,1,1,1)

```


# Processing

## H1: GCB is the most central node

### Estimation and network plotting

```{r}
# Network estimation and plotting

# Loop 
for (country_name in names(country_data)) {
  
  # Access country data
  country_matrix <- country_data[[country_name]]
  
  # Network estimation 
  mgm_result <- mgm(country_matrix, type = type, level = level,
                    lambdaSel = "EBIC", ruleReg = "OR", verbose = FALSE, pbar = F)
  
  # Path and name
  output_path <- here("Output", "Country_networks", "H1", paste0(country_name))
  
  # Plot 
  qgraph(
    mgm_result$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = country_name, edge.color = mgm_result$pairwise$edgecolor_cb,
    vTrans = 180, borders = TRUE, vsize = 11, esize = 11, label.cex = 0.60,
    label.scale = F
    #, filetype = "jpg", filename = output_path
    )
}
```

### Bootstrapped network estimation

```{r}
# mgm boots by country

# # Empty list 
# boot_results <- list()
# 
# # Loop for country 
# for (country_name in names(country_data)) {
#   
#   # Access country data 
#   country_matrix <- country_data[[country_name]]
#   
#   # Bootstrapp
#   boot_result <- bootnet(
#     country_matrix,
#     nBoots = 1000,
#     nCores = 8,
#     default = "mgm",
#     statistics = "strength"
#   )
#   
#   # Save results 
#   boot_results[[country_name]] <- boot_result
# }
# 
# 
# # Save locally
# saveRDS(boot_results, here("Input", "Secondary", "boot_H1.rds"))

# Load to save time
boot_results = readRDS(here("Input", "Secondary", "boot_H1.rds")) 
```

### H1 plot: comparison of bootstrapped centrality scores

```{r}
# Data managment of bootstrap object

# Nodes
node_names <- c("rad_poison", "aids_cia", "elf_mindcontrol", "chemtrails",
                "un_worldgov", "rothschild_control", "monsanto_gmo", 
                "ebola_bigpharma", "GCB")

# Empty list
boot_dataframes <- list()

# Loop for country
for (country_name in names(boot_results)) {
  
  # Extract the vector of 9000 values 
  values <- boot_results[[country_name]][["bootTable"]][["value"]]
  
  # Check if the length of values is divisible by 9
  if (length(values) %% length(node_names) != 0) {
    stop(paste("Length of values for", country_name, "is not a multiple of", length(node_names)))
  }
  
  # Reshape the values into a matrix with 9 columns
  values_matrix <- matrix(values, ncol = length(node_names), byrow = TRUE)
  
  # Convert the matrix into a data frame 
  values_dataframe <- as.data.frame(values_matrix)
  colnames(values_dataframe) <- node_names
  
  # Add the country-specific data frame to the list
  boot_dataframes[[country_name]] <- values_dataframe
}
```

```{r, fig.width=14, fig.height=14, out.width="100%", fig.align='center'}
# Plot for H1

# Gather centrality score in long format
long_boot_data <- do.call(rbind, lapply(names(boot_dataframes), function(country_name) {
  df <- boot_dataframes[[country_name]]
  df$country <- country_name # Add a column for the country
  return(df)
})) %>%
  melt(id.vars = "country", variable.name = "Node", value.name = "Centrality")  

# Calculate 95% bootstrapped CIs
ci_data <- long_boot_data %>%
  group_by(country, Node) %>%
  summarise(
    lower = quantile(Centrality, probs = 0.025),
    upper = quantile(Centrality, probs = 0.975),
    .groups = "drop"
  )

# Colors 
violin_colors <- ifelse(unique(long_boot_data$Node) == "GCB", "#008B8BB3", "#966FD6B3")

# Plot
H1 = ggplot(long_boot_data, aes(x = Node, y = Centrality, fill = Node)) +
  geom_violin(alpha = 0.8) +
  geom_errorbar(data = ci_data, aes(x = Node, ymin = lower, ymax = upper), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  scale_fill_manual(values = setNames(violin_colors, unique(long_boot_data$Node))) +
  facet_wrap(~ country, scales = "free_y") +  
  theme_minimal() +
  labs(
    title = "",
    x = "Node",
    y = "Centrality"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none")

# Save
ggsave(here("Output", "H1.jpg"), width = 14, height = 14, dpi = 300)

H1
```


## H2: GCB models the connectivity pof the CB networks

Moderated network models available at: https://github.com/arturobertero/Net_consp/tree/main/Output/Country_networks/H2

```{r}
# Initialize a list to store mgm_mod objects
mgm_mod_list_GCB <- list()

# Loop through each country in country_data
for (country_name in names(country_data)) {
  
  # Fit the moderated mgm for the current country
  mgm_mod <- mgm(
    data = country_data[[country_name]],
    type = rep("g", 9),
    level = rep(1, 9),
    lambdaSel = "EBIC",
    ruleReg = "OR",
    moderators = 9,
    threshold = "none",
    pbar = FALSE,
    verbose = F
  )
  
  # Store the fitted mgm_mod object in the list
  mgm_mod_list_GCB[[country_name]] <- mgm_mod
  
  # Conditioning
  cond1 <- condition(object = mgm_mod, values = list('9' = 1))
  cond3 <- condition(object = mgm_mod, values = list('9' = 3))
  cond5 <- condition(object = mgm_mod, values = list('9' = 5))
  
  # Save the combined plots
  output_path <- here("Output", "Country_networks", "H2", "GCB", paste0(country_name, ".jpg"))
  jpeg(output_path, height = 3000, width = 4000, quality = 100)
  
  # Create a 3-row layout for the plots
  par(mfrow = c(1, 3), mar = c(5, 5, 4, 2))  # Adjust margins for better visibility
  
  # Plot GCB = 1
  qgraph(
    cond1$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": GCB = 1"),
    edge.color = cond1$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot GCB = 3
  qgraph(
    cond3$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": GCB = 3"),
    edge.color = cond3$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot GCB = 5
  qgraph(
    cond5$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": GCB = 5"),
    edge.color = cond5$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  dev.off()  # Close the plotting device
}
```


## H2, rival: other factors are the true moderators

### POP

```{r}
# Initialize a list to store mgm_mod objects
mgm_mod_list_POP <- list()

# Loop through each country in country_data
for (country_name in names(country_data2)) {
  
  # Fit the moderated mgm for the current country
  mgm_mod <- mgm(
    data = country_data2[[country_name]],
    type = rep("g", 9),
    level = rep(1, 9),
    lambdaSel = "EBIC",
    ruleReg = "OR",
    moderators = 9,
    threshold = "none",
    pbar = FALSE, 
    verbose = F
  )
  
  # Store the fitted mgm_mod object in the list
  mgm_mod_list_POP[[country_name]] <- mgm_mod
  
  # Conditioning
  cond1 <- condition(object = mgm_mod, values = list('9' = 1))
  cond3 <- condition(object = mgm_mod, values = list('9' = 3))
  cond5 <- condition(object = mgm_mod, values = list('9' = 5))
  
  # Save the combined plots
  output_path <- here("Output", "Country_networks", "H2", "POP", paste0(country_name, ".jpg"))
  jpeg(output_path, height = 3000, width = 4000, quality = 100)
  
  # Create a 3-row layout for the plots
  par(mfrow = c(1, 3), mar = c(5, 5, 4, 2))  # Adjust margins for better visibility
  
  # Plot POP = 1
  qgraph(
    cond1$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": POP = 1"),
    edge.color = cond1$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot POP = 3
  qgraph(
    cond3$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": POP = 3"),
    edge.color = cond3$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot POP = 5
  qgraph(
    cond5$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": POP = 5"),
    edge.color = cond5$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  dev.off()  # Close the plotting device
}

```

### VIC

```{r}
# Initialize a list to store mgm_mod objects
mgm_mod_list_VIC <- list()

# Loop through each country in country_data
for (country_name in names(country_data3)) {
  
  # Fit the moderated mgm for the current country
  mgm_mod <- mgm(
    data = country_data3[[country_name]],
    type = rep("g", 9),
    level = rep(1, 9),
    lambdaSel = "EBIC",
    ruleReg = "OR",
    moderators = 9,
    threshold = "none",
    pbar = FALSE, 
    verbose = F
  )
  
  # Store the fitted mgm_mod object in the list
  mgm_mod_list_VIC[[country_name]] <- mgm_mod
  
  # Conditioning
  cond1 <- condition(object = mgm_mod, values = list('9' = 1))
  cond3 <- condition(object = mgm_mod, values = list('9' = 3))
  cond5 <- condition(object = mgm_mod, values = list('9' = 5))
  
  # Save the combined plots
  output_path <- here("Output", "Country_networks", "H2", "VIC", paste0(country_name, ".jpg"))
  jpeg(output_path, height = 3000, width = 4000, quality = 100)
  
  # Create a 3-row layout for the plots
  par(mfrow = c(1, 3), mar = c(5, 5, 4, 2))  # Adjust margins for better visibility
  
  # Plot VIC = 1
  qgraph(
    cond1$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": VIC = 1"),
    edge.color = cond1$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot VIC = 3
  qgraph(
    cond3$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": VIC = 3"),
    edge.color = cond3$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot VIC = 5
  qgraph(
    cond5$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": VIC = 5"),
    edge.color = cond5$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  dev.off()  # Close the plotting device
}

```

### INST_TR

```{r}
# Initialize a list to store mgm_mod objects
mgm_mod_list_INST_TR <- list()

# Loop through each country in country_data
for (country_name in names(country_data4)) {
  
  # Fit the moderated mgm for the current country
  mgm_mod <- mgm(
    data = country_data4[[country_name]],
    type = rep("g", 9),
    level = rep(1, 9),
    lambdaSel = "EBIC",
    ruleReg = "OR",
    moderators = 9,
    threshold = "none",
    pbar = FALSE, 
    verbose = F
  )
  
  # Store the fitted mgm_mod object in the list
  mgm_mod_list_INST_TR[[country_name]] <- mgm_mod
  
  # Conditioning
  cond1 <- condition(object = mgm_mod, values = list('9' = 1))
  cond3 <- condition(object = mgm_mod, values = list('9' = 3))
  cond5 <- condition(object = mgm_mod, values = list('9' = 5))
  
  # Save the combined plots
  output_path <- here("Output", "Country_networks", "H2", "INST_TR", paste0(country_name, ".jpg"))
  jpeg(output_path, height = 3000, width = 4000, quality = 100)
  
  # Create a 3-row layout for the plots
  par(mfrow = c(1, 3), mar = c(5, 5, 4, 2))  # Adjust margins for better visibility
  
  # Plot INST_TR = 1
  qgraph(
    cond1$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": INST_TR = 1"),
    edge.color = cond1$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot INST_TR = 3
  qgraph(
    cond3$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": INST_TR = 3"),
    edge.color = cond3$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot INST_TR = 5
  qgraph(
    cond5$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": INST_TR = 5"),
    edge.color = cond5$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  dev.off()  # Close the plotting deivice
}

```

### PV

```{r}
# Initialize a list to store mgm_mod objects
mgm_mod_list_PV <- list()

# Loop through each country in country_data
for (country_name in names(country_data5)) {
  
  # Fit the moderated mgm for the current country
  mgm_mod <- mgm(
    data = country_data5[[country_name]],
    type = rep("g", 9),
    level = rep(1, 9),
    lambdaSel = "EBIC",
    ruleReg = "OR",
    moderators = 9,
    threshold = "none",
    pbar = FALSE, 
    verbose = F
  )
  
  # Store the fitted mgm_mod object in the list
  mgm_mod_list_PV[[country_name]] <- mgm_mod
  
  # Conditioning
  cond1 <- condition(object = mgm_mod, values = list('9' = 1))
  cond3 <- condition(object = mgm_mod, values = list('9' = 3))
  cond5 <- condition(object = mgm_mod, values = list('9' = 5))
  
  # Save the combined plots
  output_path <- here("Output", "Country_networks", "H2", "PV", paste0(country_name, ".jpg"))
  jpeg(output_path, height = 3000, width = 4000, quality = 100)
  
  # Create a 3-row layout for the plots
  par(mfrow = c(1, 3), mar = c(5, 5, 4, 2))  # Adjust margins for better visibility
  
  # Plot PV = 1
  qgraph(
    cond1$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": PV = 1"),
    edge.color = cond1$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot PV = 3
  qgraph(
    cond3$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": PV = 3"),
    edge.color = cond3$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot PV = 5
  qgraph(
    cond5$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": PV = 5"),
    edge.color = cond5$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  dev.off()  # Close the plotting device
}

```

### parlg_lr

```{r}
# Initialize a list to store mgm_mod objects
mgm_mod_list_parlgov_lr <- list()

# Loop through each country in country_data
for (country_name in names(country_data6)) {
  
  # Fit the moderated mgm for the current country
  mgm_mod <- mgm(
    data = country_data6[[country_name]],
    type = rep("g", 9),
    level = rep(1, 9),
    lambdaSel = "EBIC",
    ruleReg = "OR",
    moderators = 9,
    threshold = "none",
    pbar = FALSE, 
    verbose = F
  )
  
  # Store the fitted mgm_mod object in the list
  mgm_mod_list_parlgov_lr[[country_name]] <- mgm_mod
  
  # Conditioning
  cond1 <- condition(object = mgm_mod, values = list('9' = 1))
  cond3 <- condition(object = mgm_mod, values = list('9' = 3))
  cond5 <- condition(object = mgm_mod, values = list('9' = 5))
  
  # Save the combined plots
  output_path <- here("Output", "Country_networks", "H2", "parlgov_lr", paste0(country_name, ".jpg"))
  jpeg(output_path, height = 3000, width = 4000, quality = 100)
  
  # Create a 3-row layout for the plots
  par(mfrow = c(1, 3), mar = c(5, 5, 4, 2))  # Adjust margins for better visibility
  
  # Plot parlgov_lr = 1
  qgraph(
    cond1$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": parlgov_lr = 1"),
    edge.color = cond1$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot parlgov_lr = 3
  qgraph(
    cond3$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": parlgov_lr = 3"),
    edge.color = cond3$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot parlgov_lr = 5
  qgraph(
    cond5$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": parlgov_lr = 5"),
    edge.color = cond5$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  dev.off()  # Close the plotting device
}

```

### pol_int

```{r}
# Initialize a list to store mgm_mod objects
mgm_mod_list_pol_int <- list()

# Loop through each country in country_data
for (country_name in names(country_data6)) {
  
  # Fit the moderated mgm for the current country
  mgm_mod <- mgm(
    data = country_data6[[country_name]],
    type = rep("g", 9),
    level = rep(1, 9),
    lambdaSel = "EBIC",
    ruleReg = "OR",
    moderators = 9,
    threshold = "none",
    pbar = FALSE, 
    verbose = F
  )
  
  # Store the fitted mgm_mod object in the list
  mgm_mod_list_pol_int[[country_name]] <- mgm_mod
  
  # Conditioning
  cond1 <- condition(object = mgm_mod, values = list('9' = 1))
  cond3 <- condition(object = mgm_mod, values = list('9' = 3))
  cond5 <- condition(object = mgm_mod, values = list('9' = 5))
  
  # Save the combined plots
  output_path <- here("Output", "Country_networks", "H2", "pol_int", paste0(country_name, ".jpg"))
  jpeg(output_path, height = 3000, width = 4000, quality = 100)
  
  # Create a 3-row layout for the plots
  par(mfrow = c(1, 3), mar = c(5, 5, 4, 2))  # Adjust margins for better visibility
  
  # Plot pol_int = 1
  qgraph(
    cond1$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": pol_int = 1"),
    edge.color = cond1$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot pol_int = 3
  qgraph(
    cond3$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": pol_int = 3"),
    edge.color = cond3$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  # Plot pol_int = 5
  qgraph(
    cond5$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = paste0(country_name, ": pol_int = 5"),
    edge.color = cond5$pairwise$edgecolor_cb, vTrans = 180, borders = TRUE,
    vsize = 11, esize = 11, title.cex = 10
  )
  
  dev.off()  # Close the plotting device
}

```

### Plot for H2 and H2b

```{r}
# Data extraction

# List of moderation coefficient lists
mod_list_names <- c(
  "mgm_mod_list_GCB",
  "mgm_mod_list_INST_TR",
  "mgm_mod_list_parlgov_lr",
  "mgm_mod_list_pol_int",
  "mgm_mod_list_POP",
  "mgm_mod_list_PV",
  "mgm_mod_list_VIC"
)

# Initialize the general list
mod_general_list <- list()

# Loop over each moderation list
for (mod_list_name in mod_list_names) {
  
  # Get the name for the second-level key
  mod_name <- sub("mgm_mod_list_", "", mod_list_name)
  
  # Initialize the second-level list
  mod_general_list[[mod_name]] <- list()
  
  # Access the moderation list by name
  mod_list <- get(mod_list_name)
  
  # Loop through each country in the moderation list
  for (country_name in names(mod_list)) {
    
    # Access the specific matrix or vector for the country
    interaction_matrix <- mod_list[[country_name]][["interactions"]][["indicator"]][[2]]
    
    # Check for valid data and count rows appropriately
    if (is.null(interaction_matrix) || length(interaction_matrix) == 0) {
      n_interactions <- 0  # No interactions
    } else if (is.vector(interaction_matrix)) {
      n_interactions <- 1  # Single row is treated as one interaction
    } else {
      n_interactions <- nrow(interaction_matrix)  # Count rows in a matrix
    }
    
    # Store the result in the corresponding country
    mod_general_list[[mod_name]][[country_name]] <- n_interactions
  }
}
```

```{r, fig.width=14, fig.height=14, out.width="100%", fig.align='center'}
# Country color palette
country_colors <- c(
  "DEU" = "#E41A1C", "ESP" = "#377EB8", "FRA" = "#4DAF4A", 
  "GBR" = "#984EA3", "ITA" = "#FF7F00", "POL" = "#ffcf33", "SWE" = "#A65628"
)

# Convert `mod_general_list` to a long data frame
mod_data <- do.call(rbind, lapply(names(mod_general_list), function(moderator) {
  data.frame(
    Moderator = moderator,
    Country = names(mod_general_list[[moderator]]),
    Interactions = unlist(mod_general_list[[moderator]], use.names = FALSE)
  )
})) %>%
  filter(Interactions > 0)  # Only include non-zero interactions

# Plot using ggplot2
interaction_plot <- ggplot(mod_data, aes(x = Country, y = Interactions, fill = Country)) +
  geom_bar(stat = "identity", color = "black") +  # Bars represent counts directly
  facet_wrap(~ Moderator, scales = "free_y") +    # Facet by Moderator
  scale_fill_manual(values = country_colors) +    # Use predefined country colors
  scale_y_continuous(limits = c(0, 6), breaks = 0:6) +  # Consistent y-axis scale and integer ticks
  theme_minimal() +
  labs(
    title = "Significant Moderations of CB networks, by Moderator and Country",
    x = "Country",
    y = "Count of Significant Interactions",
    fill = "Country"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )


# Save the plot
ggsave(here("Output", "H2_H2b.jpg"), interaction_plot, width = 12, height = 12)

interaction_plot
```


## H1b: CB index is a latent variable for mentality

```{r}
# remove all obj
rm(list = ls())

# Import data and clean
country_data_h1b = readRDS(here("Input", "Secondary", "country_data_h1b.rds"))
country_data_h1b <- lapply(country_data_h1b, function(sublist) as.matrix(sublist))

# Objects for h1b
shortnames_h1b = c("government", "aliens", "technology", "elite", "drugs", "CB")

Totalgroup_comm_h1b <- list(
  "Conspiracy Mentality" = c(1:5),
  "Conspiracy Beliefs" = c(6))

Totalgroup_cols_h1b <- c("#008B8BB3", "#966FD6B3") 

#type
type_h1b = c("g","g","g","g","g","g")

#level
level_h1b = c(1,1,1,1,1,1)
```

### Estimation and network plotting

```{r}
# Network estimation and plotting

# Loop 
for (country_name in names(country_data_h1b)) {
  
  # Access country data
  country_matrix <- country_data_h1b[[country_name]]
  
  # Network estimation 
  mgm_result <- mgm(country_matrix, type = type_h1b, level = level_h1b,
                    lambdaSel = "EBIC", ruleReg = "OR", verbose = F, pbar = F)
  
  # Path and name
  output_path <- here("Output", "Country_networks", "H1b", paste0(country_name))
  
  # Plot 
  qgraph(
    mgm_result$pairwise$wadj, layout = 'spring', labels = shortnames_h1b,
    groups = Totalgroup_comm_h1b, color = Totalgroup_cols_h1b, legend = FALSE,
    title = country_name, edge.color = mgm_result$pairwise$edgecolor_cb,
    vTrans = 180, borders = TRUE, vsize = 11, esize = 11, label.cex = 0.60,
    label.scale = F
    #, filetype = "jpg", filename = output_path
    )
}
```

### Bootstrapped network estimation

```{r}
# mgm boots by country
 
# # Empty list for bootstrapped results
# boot_result_h1b <- list()
# 
# # Loop for each country
# for (country_name in names(country_data_h1b)) {
#   
#   # Access country data
#   country_matrix <- country_data_h1b[[country_name]]
#   
#   # Bootstrapping
#   boot_result <- bootnet(
#     country_matrix,
#     nBoots = 1000,
#     nCores = 8,
#     default = "mgm",
#     statistics = "strength"
#   )
#   
#   # Save results in the list
#   boot_result_h1b[[country_name]] <- boot_result
# }
# 
# # Save locally
# saveRDS(boot_result_h1b, here("Input", "Secondary", "boot_H1b.rds"))

# To save time, load bootstrapped results
boot_result_h1b <- readRDS(here("Input", "Secondary", "boot_H1b.rds"))
```

### H1b plot

```{r}
# Data managment of bootstrap object

# Nodes
node_names <- c("government", "aliens", "technology", "elite", "drugs", "CB")

# Empty list
boot_dataframes <- list()

# Loop for each country
for (country_name in names(boot_result_h1b)) {
  
  # Extract the vector of bootstrap values
  values <- boot_result_h1b[[country_name]][["bootTable"]][["value"]]
  
  # Check if the length of values is divisible by the number of nodes
  if (length(values) %% length(node_names) != 0) {
    stop(paste("Length of values for", country_name, "is not a multiple of", length(node_names)))
  }
  
  # Reshape the values into a matrix with 6 columns (one for each node)
  values_matrix <- matrix(values, ncol = length(node_names), byrow = TRUE)
  
  # Convert the matrix into a data frame
  values_dataframe <- as.data.frame(values_matrix)
  colnames(values_dataframe) <- node_names
  
  # Add the country-specific data frame to the list
  boot_dataframes[[country_name]] <- values_dataframe
}
```

```{r, fig.width=14, fig.height=14, out.width="100%", fig.align='center'}
# Plot for H1b

# Gather centrality scores in long format
long_boot_data <- do.call(rbind, lapply(names(boot_dataframes), function(country_name) {
  df <- boot_dataframes[[country_name]]
  df$country <- country_name # Add a column for the country
  return(df)
})) %>%
  melt(id.vars = "country", variable.name = "Node", value.name = "Centrality")

# Calculate 95% bootstrapped CIs
ci_data <- long_boot_data %>%
  group_by(country, Node) %>%
  summarise(
    lower = quantile(Centrality, probs = 0.025),
    upper = quantile(Centrality, probs = 0.975),
    .groups = "drop"
  )

# Colors
violin_colors <- ifelse(unique(long_boot_data$Node) == "CB", "#966FD6B3","#008B8BB3")

# Plot
H1b <- ggplot(long_boot_data, aes(x = Node, y = Centrality, fill = Node)) +
  geom_violin(alpha = 0.8) +
  geom_errorbar(data = ci_data, aes(x = Node, ymin = lower, ymax = upper), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  scale_fill_manual(values = setNames(violin_colors, unique(long_boot_data$Node))) +
  facet_wrap(~ country, scales = "free_y") +  
  theme_minimal() +
  labs(
    title = "",
    x = "Node",
    y = "Centrality"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )

# Save
ggsave(here("Output", "H1b.jpg"), H1b, width = 14, height = 14, dpi = 300)

H1b
```
