---
title: "Centrality hypotheses, Connectivity hypotheses"
author: Arturo Bertero
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
date: "2024-12-11"
---

```{r}
knitr::opts_chunk$set(
  echo = TRUE,
  results = "markup", 
  warning = FALSE,  
  message = FALSE   
)

```

```{r}
#Libraries
library(pacman)
p_load(lavaan, rio, tidyverse, psych, here, stargazer, summarytools, visdat,
       EGAnet, qgraph, ggplot2, haven, janitor, readxl, labelled, reshape2,
       openxlsx, mgm, bootnet, conflicted, magick, patchwork)

#Options
rm(list = ls())
options(scipen = 999)
#conflicts
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::select)
```

# Input

```{r}
# Import cleaned data
data = readRDS(here("Input", "Secondary", "data.rds"))
```

```{r}
# Means by country
means_by_country <- data %>%
  group_by(country) %>%
  summarise(
    mean_CB = mean(CB, na.rm = TRUE),
    mean_GCB = mean(GCB, na.rm = TRUE)
  )

```


## Smaller country dataset for networks

```{r}
# List with country dataset 

#H1: cbs+GCB
H1 = data %>% 
 select(cb_1:cb_8, GCB, country) %>% 
 na.omit()
H1_split_data <- split(H1[, setdiff(names(H1), "country")], H1$country)

#H2: gcbs+CB
H2 = data %>% 
 select(gcb_1:gcb_5, CB, country) %>% 
 na.omit()
H2_split_data <- split(H2[, setdiff(names(H2), "country")], H2$country)

```

```{r}
#Country_data obj as matrix
H1_split_data <- lapply(H1_split_data, function(sublist) as.matrix(sublist))
H2_split_data <- lapply(H2_split_data, function(sublist) as.matrix(sublist))
```

```{r}
# objects for network 
shortnames = c("rad_food","aids","elf","chemtrails",
              "worldgov","rothschild","monsanto","ebola", "CM")

# Country color palette 
country_colors <- c(
  "DEU" = "#E41A1C", "ESP" = "#377EB8", "FRA" = "#4DAF4A", 
  "GBR" = "#984EA3", "ITA" = "#FF7F00", "POL" = "#ffcf33",
  "SWE" = "#A65628", "USA" = "#008080")

Totalgroup_comm <- list(
  "Conspiracy Beliefs" = c(1:8),
  "Conspiracy Mentality" = c(9))

Totalgroup_cols <- c("#966FD6", "#006B3C") 

#type
type = c("g","g","g","g","g","g","g","g","g")

#level
level = c(1,1,1,1,1,1,1,1,1)

```


# Processing

## H1: GCB is the most central node

### Estimation and network plotting

```{r}
#Network estimation and plotting

# Compute the average layout across all networks in H0_split_data
graph_matrices <- lapply(H1_split_data, as.matrix)

# Fit MGM models and extract adjacency matrices for layout computation
mgm_models <- lapply(graph_matrices, function(mat) {
  mgm(mat, type = type, level = level, lambdaSel = "CV", ruleReg = "OR")
})

# Extract adjacency matrices
adjacency_matrices <- lapply(mgm_models, function(model) model$pairwise$wadj)

# Compute the average layout using spring layout
shared_layout <- averageLayout(adjacency_matrices, layout = "spring")

# Loop through each country in H0_split_data
for (country_name in names(H1_split_data)) {
  
  # Access country data
  country_matrix <- H1_split_data[[country_name]]
  
  # Network estimation
  mgm_result <- mgm(
    country_matrix, type = type, level = level,
    lambdaSel = "CV", ruleReg = "OR", verbose = FALSE, pbar = FALSE
  )
  
  # Predictability
  pred_result <- predict(object = mgm_result, data = country_matrix, errorCon = 'R2')
  
  # Define output path
  output_path <- here("Output", "Country_networks", "H1", paste0(country_name, ".jpg"))

  # Open a JPG device 
  jpeg(output_path, width = 4.15, height = 5.85, units = "in", res = 600)

  # Generate the qgraph plot 
  qgraph(
    mgm_result$pairwise$wadj, layout = shared_layout, labels = shortnames,
    groups = Totalgroup_comm,  
    color = Totalgroup_cols, legend = FALSE,
    title = country_name, edge.color = mgm_result$pairwise$edgecolor_cb,
    vTrans = 180, borders = TRUE, vsize = 10, esize = 7, label.cex = 0.50,
    label.scale = FALSE, 
    pie = pred_result$errors[,2], 
    pieColor = rep('#FFFF00', length(shortnames))
  )

  dev.off()
}

```

```{r}
# Define input directory
input_directory <- here("Output", "Country_networks", "H1")

# Define output file paths
output_file_1 <- here("Output", "Supplement", "H1_Net_comp_1.jpg")
output_file_2 <- here("Output", "Supplement", "H1_Net_comp_2.jpg")

# Read and preserve full resolution of images
network_images <- lapply(
  list.files(input_directory, pattern = "\\.jpg$", full.names = TRUE),
  function(file) image_read(file)
)

# Ensure there are at least 8 images 
if (length(network_images) >= 8) {
  
  # Split images into two groups of 4
  network_images_1 <- network_images[1:4]  
  network_images_2 <- network_images[5:8]  
  
  # Create first composite image (2x4 layout)
  composite_image_1 <- image_montage(
    image_join(network_images_1),
    tile = "2x4",
    geometry = "+20+20"
  )

  # Create second composite image (2x4 layout)
  composite_image_2 <- image_montage(
    image_join(network_images_2),
    tile = "2x4",
    geometry = "+20+20"
  )

  # Save the first 
  image_write(composite_image_1, path = output_file_1, format = "jpg", quality = 100)

  # Save the second 
  image_write(composite_image_2, path = output_file_2, format = "jpg", quality = 100)

}

```

```{r}
# Print USA network with different layout to assemble Figure 1
  
  # Network estimation
  mgm_result <- mgm(H1_split_data$USA, type = type, level = level,
                    lambdaSel = "CV", ruleReg = "OR", verbose = FALSE, pbar = F)
  
  # Predictability
  pred_result <- predict(object = mgm_result, data = country_matrix, errorCon = 'R2')
  
  # Define save path
  output_path <- here("Output", "Country_networks", "H1", "USA_Fig1.jpg")

  # Open a JPG device 
  jpeg(here("Output", "Country_networks", "H1", "USA_Fig1.jpg"),
        width = 8.3, height = 3.9, units = "in", res = 600)

  # Generate the qgraph plot
  qgraph(
  mgm_result$pairwise$wadj, layout = 'spring', labels = shortnames,
  groups = Totalgroup_comm,  
  color = Totalgroup_cols, legend = FALSE,
  title = "H1: CM index and CB items", edge.color = mgm_result$pairwise$edgecolor_cb,
  vTrans = 180, borders = TRUE, vsize = 9.5, esize = 7, label.cex = 0.60,
  label.scale = F, 
  pie = pred_result$errors[,2], 
  pieColor = rep('#FFFF00', length(shortnames))
  )

  dev.off()

```

### Bootstrapped network estimation

```{r}
# mgm boots by country

# # Empty list 
# boot_results <- list()
# 
# # Loop for country 
# for (country_name in names(H1_split_data)) {
#  
#  # Access country data 
#  country_matrix <- H1_split_data[[country_name]]
#  
#  # Bootstrapp
#  boot_result <- bootnet(
#    country_matrix,
#    nBoots = 1000,
#    nCores = 8,
#    default = "mgm",
#    statistics = "strength"
#  )
#  
#  # Save results 
#  boot_results[[country_name]] <- boot_result
# }
# 
# 
# # Save locally
# saveRDS(boot_results, here("Input", "Secondary", "boot_H1.rds"))

# Load to save time
boot_results = readRDS(here("Input", "Secondary", "boot_H1.rds")) 
```

### H1 plot: comparison of bootstrapped centrality scores

```{r}
# Data managment of bootstrap object

# Nodes
node_names <- c("rad_food","aids","elf","chemtrails",
              "worldgov","rothschild","monsanto","ebola", "CM")

# Empty list
boot_dataframes <- list()

# Loop for country
for (country_name in names(boot_results)) {
  
  # Extract the vector of 9000 values 
  values <- boot_results[[country_name]][["bootTable"]][["value"]]
  
  # Check if the length of values is divisible by 9
  if (length(values) %% length(node_names) != 0) {
    stop(paste("Length of values for", country_name, "is not a multiple of", length(node_names)))
  }
  
  # Reshape the values into a matrix with 9 columns
  values_matrix <- matrix(values, ncol = length(node_names), byrow = TRUE)
  
  # Convert the matrix into a data frame 
  values_dataframe <- as.data.frame(values_matrix)
  colnames(values_dataframe) <- node_names
  
  # Add the country-specific data frame to the list
  boot_dataframes[[country_name]] <- values_dataframe
}
```

```{r}
# Plot for H1

# Gather centrality score in long format
long_boot_data <- do.call(rbind, lapply(names(boot_dataframes), function(country_name) {
  df <- boot_dataframes[[country_name]]
  df$country <- country_name # Add a column for the country
  return(df)
})) %>%
  melt(id.vars = "country", variable.name = "Node", value.name = "Centrality")  

# Calculate 95% bootstrapped CIs
ci_data <- long_boot_data %>%
  group_by(country, Node) %>%
  summarise(
    lower = quantile(Centrality, probs = 0.025),
    upper = quantile(Centrality, probs = 0.975),
    .groups = "drop"
  )

# Colors 
violin_colors <- ifelse(unique(long_boot_data$Node) == "CM", "#006B3C", "#966FD6")

# Plot
H1_plot = ggplot(long_boot_data, aes(x = Node, y = Centrality, fill = Node)) +
  geom_violin(alpha = 0.8) +
  geom_errorbar(data = ci_data, aes(x = Node, ymin = lower, ymax = upper), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  scale_fill_manual(values = setNames(violin_colors, unique(long_boot_data$Node))) +
  facet_wrap(~ country, scales = "free_y", ncol = 2, nrow = 4) +  
  labs(
    title = "",
    x = "Node",
    y = "Centrality"
  ) +
  theme(
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.title.x = element_text(size = 14, face = "bold"),
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none")

# Save
ggsave(here("Output", "H1.jpg"), width = 8.3, height = 11.7, units = "in", dpi = 300)

```


## H2: CB index is a latent variable for mentality

```{r}
# Objects for H2
shortnames_H2 = c("government", "aliens", "technology", "elite", "drugs", "CB")

Totalgroup_comm_H2 <- list(
  "Conspiracy Mentality" = c(1:5),
  "Conspiracy Beliefs" = c(6))

Totalgroup_cols_H2 <- c("#006B3C", "#966FD6") 

#type
type_H2 = c("g","g","g","g","g","g")

#level
level_H2 = c(1,1,1,1,1,1)
```

### Estimation and network plotting

```{r}
#Network estimation and plotting

# Compute the average layout across all networks in H0_split_data
graph_matrices <- lapply(H2_split_data, as.matrix)

# Fit MGM models and extract adjacency matrices for layout computation
mgm_models <- lapply(graph_matrices, function(mat) {
  mgm(mat, type = type_H2, level = level_H2, lambdaSel = "CV", ruleReg = "OR")
})

# Extract adjacency matrices
adjacency_matrices <- lapply(mgm_models, function(model) model$pairwise$wadj)

# Compute the average layout using spring layout
shared_layout <- averageLayout(adjacency_matrices, layout = "spring")

# Loop through each country in H0_split_data
for (country_name in names(H2_split_data)) {
  
  # Access country data
  country_matrix <- H2_split_data[[country_name]]
  
  # Network estimation
  mgm_result <- mgm(
    country_matrix, type = type_H2, level = level_H2,
    lambdaSel = "CV", ruleReg = "OR", verbose = FALSE, pbar = FALSE
  )
  
  # Predictability
  pred_result <- predict(object = mgm_result, data = country_matrix, errorCon = 'R2')
  
  # Define output path
  output_path <- here("Output", "Country_networks", "H2", paste0(country_name, ".jpg"))

  # Open a JPG device 
  jpeg(output_path, width = 4.15, height = 5.85, units = "in", res = 600)

  # Generate the qgraph plot 
  qgraph(
    mgm_result$pairwise$wadj, layout = shared_layout, labels = shortnames_H2,
    groups = Totalgroup_comm_H2,  
    color = Totalgroup_cols_H2, legend = FALSE,
    title = country_name, edge.color = mgm_result$pairwise$edgecolor_cb,
    vTrans = 180, borders = TRUE, vsize = 10, esize = 7, label.cex = 0.50,
    label.scale = FALSE, 
    pie = pred_result$errors[,2], 
    pieColor = rep('#FFFF00', length(shortnames_H2))
  )

  dev.off()
}

```

```{r}
# Define input directory
input_directory <- here("Output", "Country_networks", "H2")

# Define output file paths
output_file_1 <- here("Output", "Supplement", "H2_Net_comp_1.jpg")
output_file_2 <- here("Output", "Supplement", "H2_Net_comp_2.jpg")

# Read and preserve full resolution of images
network_images <- lapply(
  list.files(input_directory, pattern = "\\.jpg$", full.names = TRUE),
  function(file) image_read(file)
)

# Ensure there are at least 8 images 
if (length(network_images) >= 8) {
  
  # Split images into two groups of 4
  network_images_1 <- network_images[1:4]  
  network_images_2 <- network_images[5:8]  
  
  # Create first composite image (2x4 layout)
  composite_image_1 <- image_montage(
    image_join(network_images_1),
    tile = "2x4",
    geometry = "+20+20"
  )

  # Create second composite image (2x4 layout)
  composite_image_2 <- image_montage(
    image_join(network_images_2),
    tile = "2x4",
    geometry = "+20+20"
  )

  # Save the first 
  image_write(composite_image_1, path = output_file_1, format = "jpg", quality = 100)

  # Save the second 
  image_write(composite_image_2, path = output_file_2, format = "jpg", quality = 100)

}

```

```{r}
# Print USA network with different layout to assemble Figure 1
  
  # Network estimation
  mgm_result <- mgm(H2_split_data$USA, type = type_H2, level = level_H2,
                    lambdaSel = "CV", ruleReg = "OR", verbose = FALSE, pbar = F)
  
  # Predictability
  pred_result <- predict(object = mgm_result, data = country_matrix, errorCon = 'R2')
  
  # Define save path
  output_path <- here("Output", "Country_networks", "H2", "USA_Fig1.jpg")

  # Open a JPG device 
  jpeg(here("Output", "Country_networks", "H2", "USA_Fig1.jpg"),
        width = 8.3, height = 3.9, units = "in", res = 600)

  # Generate the qgraph plot
  qgraph(
  mgm_result$pairwise$wadj, layout = 'spring', labels = shortnames_H2,
  groups = Totalgroup_comm_H2,  
  color = Totalgroup_cols_H2, legend = FALSE,
  title = "H2: CB index and CM items", edge.color = mgm_result$pairwise$edgecolor_cb,
  vTrans = 180, borders = TRUE, vsize = 9.5, esize = 7, label.cex = 0.60,
  label.scale = F, 
  pie = pred_result$errors[,2], 
  pieColor = rep('#FFFF00', length(shortnames_H2))
  )

  dev.off()

```

### Bootstrapped network estimation

```{r}
# mgm boots by country
 
# # Empty list for bootstrapped results
# boot_result_H2 <- list()
# 
# # Loop for each country
# for (country_name in names(H2_split_data)) {
#   
#   # Access country data
#   country_matrix <- H2_split_data[[country_name]]
#   
#   # Bootstrapping
#   boot_result <- bootnet(
#     country_matrix,
#     nBoots = 1000,
#     nCores = 8,
#     default = "mgm",
#     statistics = "strength"
#   )
#   
#   # Save results in the list
#   boot_result_H2[[country_name]] <- boot_result
# }
# 
# # Save locally
# saveRDS(boot_result_H2, here("Input", "Secondary", "boot_H2.rds"))

# To save time, load bootstrapped results
boot_result_H2 <- readRDS(here("Input", "Secondary", "boot_H2.rds"))
```

### H2 plot

```{r}
# Data managment of bootstrap object

# Nodes
node_names <- c("government", "aliens", "technology", "elite", "drugs", "CB")

# Empty list
boot_dataframes <- list()

# Loop for each country
for (country_name in names(boot_result_H2)) {
  
  # Extract the vector of bootstrap values
  values <- boot_result_H2[[country_name]][["bootTable"]][["value"]]
  
  # Check if the length of values is divisible by the number of nodes
  if (length(values) %% length(node_names) != 0) {
    stop(paste("Length of values for", country_name, "is not a multiple of", length(node_names)))
  }
  
  # Reshape the values into a matrix with 6 columns (one for each node)
  values_matrix <- matrix(values, ncol = length(node_names), byrow = TRUE)
  
  # Convert the matrix into a data frame
  values_dataframe <- as.data.frame(values_matrix)
  colnames(values_dataframe) <- node_names
  
  # Add the country-specific data frame to the list
  boot_dataframes[[country_name]] <- values_dataframe
}
```

```{r}
# Plot for H2

# Gather centrality scores in long format
long_boot_data <- do.call(rbind, lapply(names(boot_dataframes), function(country_name) {
  df <- boot_dataframes[[country_name]]
  df$country <- country_name 
  return(df)
})) %>%
  melt(id.vars = "country", variable.name = "Node", value.name = "Centrality")

# Calculate 95% bootstrapped CIs
ci_data <- long_boot_data %>%
  group_by(country, Node) %>%
  summarise(
    lower = quantile(Centrality, probs = 0.025),
    upper = quantile(Centrality, probs = 0.975),
    .groups = "drop"
  )

# Colors
violin_colors <- ifelse(unique(long_boot_data$Node) == "CB", "#966FD6","#006B3C")

# Plot
H2 <- ggplot(long_boot_data, aes(x = Node, y = Centrality, fill = Node)) +
  geom_violin(alpha = 0.8) +
  geom_errorbar(data = ci_data, aes(x = Node, ymin = lower, ymax = upper), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  scale_fill_manual(values = setNames(violin_colors, unique(long_boot_data$Node))) +
  facet_wrap(~ country, scales = "free_y", ncol = 2, nrow = 4) +  
  labs(
    title = "",
    x = "Node",
    y = "Centrality"
  ) +
  theme(
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.title.x = element_text(size = 14, face = "bold"),
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none")

# Save
ggsave(here("Output", "H2.jpg"), H2, width = 8.3, height = 11.7, units = "in", dpi = 300)

```

## Figure_1

```{r}
# Define the input file paths
file_H0 <- here("Output", "Country_networks", "H0", "USA_Fig1.jpg")
file_H1 <- here("Output", "Country_networks", "H1", "USA_Fig1.jpg")
file_H2 <- here("Output", "Country_networks", "H2", "USA_Fig1.jpg")

# Define output file path
output_file_long <- here("Output", "Figure_1_Long.jpg")

# Read images
network_images <- lapply(
  c(file_H0, file_H1, file_H2),
  function(file) image_read(file)
)

# Create a long image 
composite_image_long <- image_append(image_join(network_images), stack = TRUE)

# Save with max quality
image_write(
  composite_image_long, 
  path = output_file_long, 
  format = "jpg", 
  quality = 600
)
```

## Figure 4

```{r}
## List with country dataset 

# For H1
#CB
CB = data %>% 
 select(cb_1:cb_8, country) %>% 
 na.omit()
CB_split_data <- split(CB[, setdiff(names(CB), "country")], CB$country)

#H1: cbs+GCB
H1 = data %>% 
 select(cb_1:cb_8, GCB, country) %>% 
 na.omit()
H1_split_data <- split(H1[, setdiff(names(H1), "country")], H1$country)


# For H2
#GCB
GCB = data %>% 
 select(gcb_1:gcb_5, country) %>% 
 na.omit()
GCB_split_data <- split(GCB[, setdiff(names(GCB), "country")], GCB$country)

#H2: gcbs+CB
H2 = data %>% 
 select(gcb_1:gcb_5, CB, country) %>% 
 na.omit()
H2_split_data <- split(H2[, setdiff(names(H2), "country")], H2$country)
```

```{r}
# ## Bootstrap data
# 
# # Number of bootstrap samples
# n_boot <- 1000
# 
# # Function to bootstrap a matrix
# bootstrap_matrix <- function(mat, n_boot) {
#   lapply(1:n_boot, function(i) {
#     sample_indices <- sample(1:nrow(mat), replace = TRUE)  # Sample rows with #replacement
#     as.matrix(mat[sample_indices, , drop = FALSE])  # Convert to matrix
#   })
# }
# 
# # Initialize lists to store bootstrap results
# boot_CB <- list()
# boot_H1 <- list()
# boot_GCB <- list()
# boot_H2 <- list()
# 
# # Bootstrapping CB_split_data
# for (country in names(CB_split_data)) {
#   cat("Bootstrapping CB:", country, "\n")
#   boot_CB[[country]] <- bootstrap_matrix(CB_split_data[[country]], n_boot)
# }
# 
# # Bootstrapping H1_split_data
# for (country in names(H1_split_data)) {
#   cat("Bootstrapping H1:", country, "\n")
#   boot_H1[[country]] <- bootstrap_matrix(H1_split_data[[country]], n_boot)
# }
# 
# # Bootstrapping GCB_split_data
# for (country in names(GCB_split_data)) {
#   cat("Bootstrapping GCB:", country, "\n")
#   boot_GCB[[country]] <- bootstrap_matrix(GCB_split_data[[country]], n_boot)
# }
# 
# # Bootstrapping H2_split_data
# for (country in names(H2_split_data)) {
#   cat("Bootstrapping H2:", country, "\n")
#   boot_H2[[country]] <- bootstrap_matrix(H2_split_data[[country]], n_boot)
# }

```


```{r}

# ## Bootstrap R2 values
#
# # Set bootstrap iterations
# n_boot <- 1000 
# 
# # Function to apply mgm and extract node-wise R2
# apply_mgm_bootstrap <- function(boot_matrices) {
#   
#   # Get number of nodes (columns)
#   n_nodes <- ncol(boot_matrices[[1]])  
# 
#   # Initialize matrix to store R2 values 
#   r2_matrix <- matrix(NA, nrow = n_boot, ncol = n_nodes)
# 
#   for (i in seq_len(n_boot)) {
#     cat("Processing iteration:", i, "of", n_boot, "\n")
#     
#     # Convert to matrix
#     data_mat <- as.matrix(boot_matrices[[i]])
# 
#     # Fit mgm model
#     mgm_model <- mgm(
#       data = data_mat, 
#       type = rep("g", n_nodes),  # Gaussian variables
#       level = rep(1, n_nodes), 
#       lambdaSel = "CV", 
#       ruleReg = "OR",
#       verbose = F
#     )
# 
#     # R2 values
#     pred <- predict(object = mgm_model, data = data_mat, errorCon = 'R2')
# 
#     # Extract only the R2 values from the errors data frame
#     r2_values <- pred$errors$R2  
# 
#     # Store in matrix
#     r2_matrix[i, ] <- r2_values
#   }
# 
#   return(r2_matrix)  
# }
# 
# # Initialize lists to store r2 results
# r2_CB <- list()
# r2_H1 <- list()
# r2_GCB <- list()
# r2_H2 <- list()
# 
# # Apply mgm to each bootstrapped dataset
# 
# for (country in names(boot_CB)) {
#   cat("\nProcessing CB:", country, "\n")
#   r2_CB[[country]] <- apply_mgm_bootstrap(boot_CB[[country]])
# }
# 
# for (country in names(boot_H1)) {
#   cat("\nProcessing H1:", country, "\n")
#   r2_H1[[country]] <- apply_mgm_bootstrap(boot_H1[[country]])
# }
# 
# for (country in names(boot_GCB)) {
#   cat("\nProcessing GCB:", country, "\n")
#   r2_GCB[[country]] <- apply_mgm_bootstrap(boot_GCB[[country]])
# }
# 
# for (country in names(boot_H2)) {
#   cat("\nProcessing H2:", country, "\n")
#   r2_H2[[country]] <- apply_mgm_bootstrap(boot_H2[[country]])
# }
# 
# # Save results locally
# saveRDS(r2_CB, here("Input", "Secondary", "r2_CB.rds"))
# saveRDS(r2_H1, here("Input", "Secondary", "r2_H1.rds"))
# saveRDS(r2_GCB, here("Input", "Secondary", "r2_GCB.rds"))
# saveRDS(r2_H2, here("Input", "Secondary", "r2_H2.rds"))

```

```{r}
# Load bootstrapped R2 to save time
r2_CB <- readRDS(here("Input", "Secondary", "r2_CB.rds"))
r2_H1 <- readRDS(here("Input", "Secondary", "r2_H1.rds")) 
r2_GCB <- readRDS(here("Input", "Secondary", "r2_GCB.rds")) 
r2_H2 <- readRDS(here("Input", "Secondary", "r2_H2.rds")) 

# Create/re-use shortnames objs
shortnames_r2_CB <- c("rad_food","aids","elf","chemtrails",
              "worldgov","rothschild","monsanto","ebola")

shortnames_r2_H1 <- shortnames

shortnames_r2_GCB <- c("government", "aliens", "technology", "elite", "drugs")

shortnames_r2_H2 <- shortnames_H2
```

### First comparison

```{r}
# Function to remove column 9 from all country lists
remove_ninth_column <- function(r2_list) {
  modified_list <- list()
  
  for (country in names(r2_list)) {
    df <- as.data.frame(r2_list[[country]])  
    
    if (ncol(df) >= 9) {  
      df <- df[, -9]  
    }
    
    modified_list[[country]] <- df  
  }
  
  return(modified_list)
}

# Apply function to remove column 9 from r2_H1
r2_H1 <- remove_ninth_column(r2_H1)

# Function to rename columns using shortnames_r2_CB
rename_columns <- function(r2_list, shortnames) {
  modified_list <- list()
  
  for (country in names(r2_list)) {
    df <- as.data.frame(r2_list[[country]])  
    
    if (ncol(df) == length(shortnames)) {  # ensure matching column count
      colnames(df) <- shortnames  # assign new column names
    } else {
      warning(paste("Mismatch in column count for", country, "- Skipping renaming"))
    }
    
    modified_list[[country]] <- df  
  }
  
  return(modified_list)
}

# Apply renaming to r2_H1 and r2_CB
r2_H1 <- rename_columns(r2_H1, shortnames_r2_CB)
r2_CB <- rename_columns(r2_CB, shortnames_r2_CB)

```

```{r}
# Function to compute the mean r2 from bootstrapped results
compute_mean_r2 <- function(r2_list) {
  mean_r2_list <- list()

  for (country in names(r2_list)) {
    df <- as.data.frame(r2_list[[country]])  
    
    # Compute the mean r2 per node
    mean_df <- df %>%
      summarise(across(everything(), mean, na.rm = TRUE)) %>%
      pivot_longer(cols = everything(), names_to = "Node", values_to = "R2") %>%
      mutate(country = country)
    
    mean_r2_list[[country]] <- mean_df
  }

  return(bind_rows(mean_r2_list))  # Combine all countries into one dataframe
}

# Compute mean r2 values for CB and H1 with correct labels
mean_r2_CB <- compute_mean_r2(r2_CB)
mean_r2_H1 <- compute_mean_r2(r2_H1)

```

```{r}
# Function to filter out nodes that are not in both lists
filter_common_nodes <- function(mean_r2_1, mean_r2_2) {
  common_nodes <- intersect(mean_r2_1$Node, mean_r2_2$Node)  # Identify common nodes
  filtered_r2_1 <- mean_r2_1 %>% filter(Node %in% common_nodes)
  filtered_r2_2 <- mean_r2_2 %>% filter(Node %in% common_nodes)

  return(list(filtered_r2_1, filtered_r2_2))
}

# Apply filtering to ensure both datasets contain the same nodes
filtered_r2_CB_H1 <- filter_common_nodes(mean_r2_CB, mean_r2_H1)
mean_r2_CB_filtered <- filtered_r2_CB_H1[[1]]
mean_r2_H1_filtered <- filtered_r2_CB_H1[[2]]

```

```{r}
# Function to prepare r2 data for lollipop plot with proper labels
prepare_r2_data <- function(r2_1, r2_2, label_1, label_2) {
  merged_df <- r2_1 %>%
    rename(R2_1 = R2) %>%
    inner_join(r2_2 %>% rename(R2_2 = R2), by = c("Node", "country"))  # Merge data on node & country

  # Rename groups and reorder labels
  merged_df <- merged_df %>%
    rename(low = R2_1, high = R2_2) %>%
    mutate(
      Group1 = label_1,
      Group2 = label_2,
      Node = factor(Node, levels = rev(shortnames_r2_CB))  # Assign correct node labels
    )

  return(merged_df)
}

# Prepare data for plotting (CB vs. CB + GCB) with correct labels
r2_comparison_df <- prepare_r2_data(mean_r2_CB_filtered, mean_r2_H1_filtered, "CB", "CB + GCB")

```

```{r}
# Function to create a lollipop plot 
create_facet_r2_plot <- function(data) {
  ggplot(data) +
    geom_segment(aes(x = Node, xend = Node, y = low, yend = high), color = "grey") +
    geom_point(aes(x = Node, y = low, color = Group1), size = 2) +  # Baseline r2
    geom_point(aes(x = Node, y = high, color = Group2), size = 2) +  # Extended r2
    coord_flip() +
    scale_color_manual(
      name = "Network Type",
      values = c("CB" = "#006B3C", "CB + GCB" = "#966FD6")  # Assign colors
    ) +
    scale_y_continuous(limits = c(0.45, 0.75)) +
    theme(
      legend.position = "bottom",
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 10),
      axis.title.y = element_text(size = 14, face = "bold"),
      axis.title.x = element_text(size = 10),
      axis.text.y = element_text(size = 11),  # Ensure node labels are readable
      axis.text.x = element_text(size = 10),
      plot.title = element_text(hjust = 0.5, size = 14, face = "bold")
    ) +
    facet_wrap(~ country, scales = "fixed", ncol = 4, nrow = 2) +
    xlab("") +
    ylab("Mean Bootstrapped R²") +
    ggtitle("Gains in R², Adding CM to the CB Networks")
}

# Generate & Print the Plot
facet_r2_plot <- create_facet_r2_plot(r2_comparison_df)
print(facet_r2_plot)


```

### Second comparison

```{r}
# Function to remove column 6 from all country lists
remove_sixth_column <- function(r2_list) {
  modified_list <- list()
  
  for (country in names(r2_list)) {
    df <- as.data.frame(r2_list[[country]])  # Convert to dataframe
    
    if (ncol(df) >= 6) {  # Ensure column 6 exists before trying to remove it
      df <- df[, -6]  # Remove the sixth column
    }
    
    modified_list[[country]] <- df  # Store modified dataframe
  }
  
  return(modified_list)
}

# Apply function to remove column 6 from `r2_H2`
r2_H2 <- remove_sixth_column(r2_H2)

# Function to rename columns using shortnames_r2_GCB
rename_columns <- function(r2_list, shortnames) {
  modified_list <- list()
  
  for (country in names(r2_list)) {
    df <- as.data.frame(r2_list[[country]])  # Convert to dataframe
    
    if (ncol(df) == length(shortnames)) {  # Ensure matching column count
      colnames(df) <- shortnames  # Assign new column names
    } else {
      warning(paste("Mismatch in column count for", country, "- Skipping renaming"))
    }
    
    modified_list[[country]] <- df  # Store modified dataframe
  }
  
  return(modified_list)
}

# Apply renaming to `r2_H2` and `r2_GCB`
r2_H2 <- rename_columns(r2_H2, shortnames_r2_GCB)
r2_GCB <- rename_columns(r2_GCB, shortnames_r2_GCB)

```

```{r}
# Function to compute the mean r2 from bootstrapped results
compute_mean_r2 <- function(r2_list) {
  mean_r2_list <- list()

  for (country in names(r2_list)) {
    df <- as.data.frame(r2_list[[country]]) 
    
    # Compute the mean r2 per node
    mean_df <- df %>%
      summarise(across(everything(), mean, na.rm = TRUE)) %>%
      pivot_longer(cols = everything(), names_to = "Node", values_to = "R2") %>%
      mutate(country = country)
    
    mean_r2_list[[country]] <- mean_df
  }

  return(bind_rows(mean_r2_list))  
}

# Compute mean r2 values for GCB and H2 with correct labels
mean_r2_GCB <- compute_mean_r2(r2_GCB)
mean_r2_H2 <- compute_mean_r2(r2_H2)

```

```{r}
# Function to compute the mean r2 from bootstrapped results
compute_mean_r2 <- function(r2_list) {
  mean_r2_list <- list()

  for (country in names(r2_list)) {
    df <- as.data.frame(r2_list[[country]])  
    
    # Compute the mean r2 per node
    mean_df <- df %>%
      summarise(across(everything(), mean, na.rm = TRUE)) %>%
      pivot_longer(cols = everything(), names_to = "Node", values_to = "R2") %>%
      mutate(country = country)
    
    mean_r2_list[[country]] <- mean_df
  }

  return(bind_rows(mean_r2_list))  
}

# Compute mean r2 values for GCB and H2 with correct labels
mean_r2_GCB <- compute_mean_r2(r2_GCB)
mean_r2_H2 <- compute_mean_r2(r2_H2)

```

```{r}
# Function to filter out nodes that are not in both lists
filter_common_nodes <- function(mean_r2_1, mean_r2_2) {
  common_nodes <- intersect(mean_r2_1$Node, mean_r2_2$Node)  # Identify common nodes
  filtered_r2_1 <- mean_r2_1 %>% filter(Node %in% common_nodes)
  filtered_r2_2 <- mean_r2_2 %>% filter(Node %in% common_nodes)

  return(list(filtered_r2_1, filtered_r2_2))
}

# Apply filtering 
filtered_r2_GCB_H2 <- filter_common_nodes(mean_r2_GCB, mean_r2_H2)
mean_r2_GCB_filtered <- filtered_r2_GCB_H2[[1]]
mean_r2_H2_filtered <- filtered_r2_GCB_H2[[2]]

```

```{r}
# Function to prepare r2 data for lollipop plot with proper labels
prepare_r2_data <- function(r2_1, r2_2, label_1, label_2) {
  merged_df <- r2_1 %>%
    rename(R2_1 = R2) %>%
    inner_join(r2_2 %>% rename(R2_2 = R2), by = c("Node", "country"))  # Merge data on node & country

  # Rename groups and reorder labels
  merged_df <- merged_df %>%
    rename(low = R2_1, high = R2_2) %>%
    mutate(
      Group1 = label_1,
      Group2 = label_2,
      Node = factor(Node, levels = rev(shortnames_r2_GCB))  # Assign correct node labels
    )

  return(merged_df)
}

# Prepare data for plotting (GCB vs. GCB + CB) with correct labels
r2_comparison_df <- prepare_r2_data(mean_r2_GCB_filtered, mean_r2_H2_filtered, "GCB", "GCB + CB")

```

```{r}
# Function to create a lollipop plot with proper formatting & adjusted x-axis scale
create_facet_r2_plot <- function(data) {
  ggplot(data) +
    geom_segment(aes(x = Node, xend = Node, y = low, yend = high), color = "grey") +
    geom_point(aes(x = Node, y = low, color = Group1), size = 2) +  # Baseline R²
    geom_point(aes(x = Node, y = high, color = Group2), size = 2) +  # Extended R²
    coord_flip() +
    scale_color_manual(
      name = "Network Type",
      values = c("GCB" = "#006B3C", "GCB + CB" = "#966FD6")  # Assign colors
    ) +
    scale_y_continuous(limits = c(0.20, 0.55)) +
    theme(
      legend.position = "bottom",
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 10),
      axis.title.y = element_text(size = 14, face = "bold"),
      axis.title.x = element_text(size = 10),
      axis.text.y = element_text(size = 11),  # Ensure node labels are readable
      axis.text.x = element_text(size = 10),
      plot.title = element_text(hjust = 0.5, size = 14, face = "bold")
    ) +
    facet_wrap(~ country, scales = "fixed", ncol = 4, nrow = 2) +  # Match previous panel settings
    xlab("") +
    ylab("Mean Bootstrapped R²") +
    ggtitle("Gains in R², Adding CB to the CM Networks")
}

# Generate & Print the Plot
facet_r2_plot2 <- create_facet_r2_plot(r2_comparison_df)
print(facet_r2_plot2)


```

### Assemble

```{r}
#Patchwork
Figure_4 = facet_r2_plot / facet_r2_plot2

# Save
ggsave(
  filename = here("Output", "Figure_4.jpg"), plot = Figure_4,
  width = 8.3, height = 11.7, dpi = 600)
```

