---
title: "Centrality hypotheses, Connectivity hypotheses"
author: Arturo Bertero
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
date: "2024-12-11"
---

```{r}
knitr::opts_chunk$set(
  echo = TRUE,
  results = "markup", # Show output
  warning = FALSE,  # Do not show warnings
  message = FALSE   # Do not show messages
)

```

```{r}
#Libraries
library(pacman)
p_load(lavaan, rio, tidyverse, psych, here, stargazer, summarytools, visdat,
       EGAnet, qgraph, ggplot2, haven, janitor, readxl, labelled, reshape2,
       openxlsx, mgm, bootnet, conflicted, magick)

#Options
rm(list = ls())
options(scipen = 999)
#conflicts
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::select)
```

# Input

## Merge US and SUSPECTS

```{r}
# Import cleaned data
data = readRDS(here("Input", "Secondary", "data.rds")) 
us = readRDS(here("Input", "Secondary", "USA_clean.rds"))
```

```{r}
#Na.omit and common structure
data = data %>% 
  select(country, POP, INST_TR, VIC, GCB, CB, gcb_1:cb_8) %>% 
  na.omit()

us = us %>% 
  select(country, POP, INST_TR, VIC, GCB, CB, gcb_1:cb_8) %>% 
  na.omit()
```

```{r}
#Append
data = bind_rows(data, us)
```

## Smaller country dataset for networks

```{r}
# List with country dataset 

#H1: cbs+GCB
H1 = data %>% 
 select(cb_1:cb_8, GCB, country) %>% 
 na.omit()
H1_split_data <- split(H1[, setdiff(names(H1), "country")], H1$country)

#H2: gcbs+CB
H2 = data %>% 
 select(gcb_1:gcb_5, CB, country) %>% 
 na.omit()
H2_split_data <- split(H2[, setdiff(names(H2), "country")], H2$country)

#H1b: gcbs+INST_TR
H1b = data %>% 
 select(cb_1:cb_8, INST_TR, country) %>% 
 na.omit()
H1b_split_data <- split(H1b[, setdiff(names(H1b), "country")], H1b$country)

#H1c: gcbs+POP
H1c = data %>% 
 select(cb_1:cb_8, POP, country) %>% 
 na.omit()
H1c_split_data <- split(H1c[, setdiff(names(H1c), "country")], H1c$country)

#H1d: gcbs+VIC
H1d = data %>% 
 select(cb_1:cb_8, VIC, country) %>% 
 na.omit()
H1d_split_data <- split(H1d[, setdiff(names(H1d), "country")], H1d$country)

#All Vs
all_data_split_data = data %>% 
 select(country, POP, INST_TR, VIC, GCB, CB) %>% 
 na.omit()
all_data_split_data <- split(all_data_split_data[, setdiff(names(all_data_split_data), "country")], all_data_split_data$country)
```

```{r}
#Country_data obj as matrix
H1_split_data <- lapply(H1_split_data, function(sublist) as.matrix(sublist))
H1b_split_data <- lapply(H1b_split_data, function(sublist) as.matrix(sublist))
H1c_split_data <- lapply(H1c_split_data, function(sublist) as.matrix(sublist))
H1d_split_data <- lapply(H1d_split_data, function(sublist) as.matrix(sublist))
H2_split_data <- lapply(H2_split_data, function(sublist) as.matrix(sublist))
all_data_split_data = lapply(all_data_split_data, function(sublist) as.matrix(sublist))
```

```{r}
# objects for network 
shortnames = c("rad_poison","aids_cia","elf_mindcontrol","chemtrails",
              "un_worldgov","rothschild_control","monsanto_gmo","ebola_bigpharma", "CM")

# Country color palette 
country_colors <- c(
  "DEU" = "#E41A1C", "ESP" = "#377EB8", "FRA" = "#4DAF4A", 
  "GBR" = "#984EA3", "ITA" = "#FF7F00", "POL" = "#ffcf33",
  "SWE" = "#A65628", "USA" = "#008080")

Totalgroup_comm <- list(
  "Conspiracy Beliefs" = c(1:8),
  "Conspiracy Mentality" = c(9))

Totalgroup_cols <- c("#966FD6B3", "#008B8BB3") 

#type
type = c("g","g","g","g","g","g","g","g","g")

#level
level = c(1,1,1,1,1,1,1,1,1)

```


# Processing

## H1: GCB is the most central node

### Estimation and network plotting

```{r}
# Network estimation and plotting

  # Loop through each country
  for (country_name in names(H1_split_data)) {
  
  # Access country data
  country_matrix <- H1_split_data[[country_name]]
  
  # Network estimation
  mgm_result <- mgm(country_matrix, type = type, level = level,
                    lambdaSel = "EBIC", ruleReg = "OR", verbose = FALSE, pbar = F)
  
  # Predictability
  pred_result <- predict(object = mgm_result, data = country_matrix, errorCon = 'R2')
  
  # Path and name
  output_path <- here("Output", "Country_networks", "H1", paste0(country_name))
  
  # Plot with R^2 visualization
  qgraph(
    mgm_result$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = country_name, edge.color = mgm_result$pairwise$edgecolor_cb,
    vTrans = 180, borders = TRUE, vsize = 11, esize = 11, label.cex = 0.60,
    label.scale = F, filetype = "jpg", filename = output_path,
    pie = pred_result$errors[,2], 
    pieColor = rep('#FFFF00', length(shortnames))
  )
}

```

```{r}
# Define input directory and output file path
input_directory <- here("Output", "Country_networks", "H1")
output_file <- here("Output", "H1_Net_comp.jpg")

# Read, scale for maximum quality, and combine all JPG files in a 4x2 layout
network_images <- lapply(
  list.files(input_directory, pattern = "\\.jpg$", full.names = TRUE),
  function(file) image_scale(image_read(file), "2000x2000") # Further increase image size
)

# Create a composite image with higher resolution and layout
composite_image <- image_montage(
  image_join(network_images),
  tile = "4x2",
  geometry = "+20+20" # Add more spacing between images
)

# Save the composite image with maximum quality
image_write(composite_image, path = output_file, format = "jpg", density = 300, quality = 100)
```

```{r}
# Define input directory and output file path
input_directory <- here("Output", "Country_networks", "H1")
output_file <- here("Output", "H1_Net_comp_long.jpg")

# Read, scale for maximum quality, and combine all JPG files in a 4x2 layout
network_images <- lapply(
  list.files(input_directory, pattern = "\\.jpg$", full.names = TRUE),
  function(file) image_scale(image_read(file), "2000x2000") # Further increase image size
)

# Create a composite image with higher resolution and layout
composite_image <- image_montage(
  image_join(network_images),
  tile = "2x4",
  geometry = "+20+20" # Add more spacing between images
)

# Save the composite image with maximum quality
image_write(composite_image, path = output_file, format = "jpg", density = 300, quality = 100)
```

### Bootstrapped network estimation

```{r}
# mgm boots by country

# # Empty list 
# boot_results <- list()
# 
# # Loop for country 
# for (country_name in names(H1_split_data)) {
#  
#  # Access country data 
#  country_matrix <- H1_split_data[[country_name]]
#  
#  # Bootstrapp
#  boot_result <- bootnet(
#    country_matrix,
#    nBoots = 1000,
#    nCores = 8,
#    default = "mgm",
#    statistics = "strength"
#  )
#  
#  # Save results 
#  boot_results[[country_name]] <- boot_result
# }
# 
# 
# # Save locally
# saveRDS(boot_results, here("Input", "Secondary", "boot_H1.rds"))

# Load to save time
boot_results = readRDS(here("Input", "Secondary", "boot_H1.rds")) 
```

### H1 plot: comparison of bootstrapped centrality scores

```{r}
# Data managment of bootstrap object

# Nodes
node_names <- c("rad_poison", "aids_cia", "elf_mindcontrol", "chemtrails",
                "un_worldgov", "rothschild_control", "monsanto_gmo", 
                "ebola_bigpharma", "CM")

# Empty list
boot_dataframes <- list()

# Loop for country
for (country_name in names(boot_results)) {
  
  # Extract the vector of 9000 values 
  values <- boot_results[[country_name]][["bootTable"]][["value"]]
  
  # Check if the length of values is divisible by 9
  if (length(values) %% length(node_names) != 0) {
    stop(paste("Length of values for", country_name, "is not a multiple of", length(node_names)))
  }
  
  # Reshape the values into a matrix with 9 columns
  values_matrix <- matrix(values, ncol = length(node_names), byrow = TRUE)
  
  # Convert the matrix into a data frame 
  values_dataframe <- as.data.frame(values_matrix)
  colnames(values_dataframe) <- node_names
  
  # Add the country-specific data frame to the list
  boot_dataframes[[country_name]] <- values_dataframe
}
```

```{r}
# Plot for H1

# Gather centrality score in long format
long_boot_data <- do.call(rbind, lapply(names(boot_dataframes), function(country_name) {
  df <- boot_dataframes[[country_name]]
  df$country <- country_name # Add a column for the country
  return(df)
})) %>%
  melt(id.vars = "country", variable.name = "Node", value.name = "Centrality")  

# Calculate 95% bootstrapped CIs
ci_data <- long_boot_data %>%
  group_by(country, Node) %>%
  summarise(
    lower = quantile(Centrality, probs = 0.025),
    upper = quantile(Centrality, probs = 0.975),
    .groups = "drop"
  )

# Colors 
violin_colors <- ifelse(unique(long_boot_data$Node) == "CM", "#008B8BB3", "#966FD6B3")

# Plot
H1_plot = ggplot(long_boot_data, aes(x = Node, y = Centrality, fill = Node)) +
  geom_violin(alpha = 0.8) +
  geom_errorbar(data = ci_data, aes(x = Node, ymin = lower, ymax = upper), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  scale_fill_manual(values = setNames(violin_colors, unique(long_boot_data$Node))) +
  facet_wrap(~ country, scales = "free_y", ncol = 2, nrow = 4) +  
  labs(
    title = "",
    x = "Node",
    y = "Centrality"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none")

# Save
ggsave(here("Output", "H1.jpg"), width = 10, height = 16, dpi = 300)

```

## H1b: INST_TR is the most central node

### Estimation and network plotting

```{r}
# Network estimation and plotting

shortnames = c("rad_poison","aids_cia","elf_mindcontrol","chemtrails",
              "un_worldgov","rothschild_control","monsanto_gmo","ebola_bigpharma", "INST_TR")

# Loop through each country
for (country_name in names(H1b_split_data)) {
  
  # Access country data
  country_matrix <- H1b_split_data[[country_name]]
  
  # Network estimation
  mgm_result <- mgm(country_matrix, type = type, level = level,
                    lambdaSel = "EBIC", ruleReg = "OR", verbose = FALSE, pbar = F)
  
  # Predictability
  pred_result <- predict(object = mgm_result, data = country_matrix, errorCon = 'R2')
  
  # Path and name
  output_path <- here("Output", "Country_networks", "H1b", paste0(country_name))
  
  # Plot with R^2 visualization
  qgraph(
    mgm_result$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = country_name, edge.color = mgm_result$pairwise$edgecolor_cb,
    vTrans = 180, borders = TRUE, vsize = 11, esize = 11, label.cex = 0.60,
    label.scale = F, filetype = "jpg", filename = output_path,
    pie = pred_result$errors[,2], # R^2 values for pies
    pieColor = rep('#FFFF00', length(shortnames)) # Yellow color for R^2 pies
  )
}
```

### Bootstrapped network estimation

```{r}
# mgm boots by country

# # Empty list 
# boot_results <- list()
# 
# # Loop for country 
# for (country_name in names(H1b_split_data)) {
# 
# # Access country data 
# country_matrix <- H1b_split_data[[country_name]]
# 
# # Bootstrapp
# boot_result <- bootnet(
#   country_matrix,
#   nBoots = 1000,
#   nCores = 8,
#   default = "mgm",
#   statistics = "strength"
# )
# 
# # Save results 
# boot_results[[country_name]] <- boot_result
# }
# 
# 
# # Save locally
# saveRDS(boot_results, here("Input", "Secondary", "boot_H1b.rds"))

# Load to save time
boot_results = readRDS(here("Input", "Secondary", "boot_H1b.rds")) 
```

### H1b plot: comparison of bootstrapped centrality scores

```{r}
# Data managment of bootstrap object

# Nodes
node_names <- c("rad_poison", "aids_cia", "elf_mindcontrol", "chemtrails",
                "un_worldgov", "rothschild_control", "monsanto_gmo", 
                "ebola_bigpharma", "INST_TR")

# Empty list
boot_dataframes <- list()

# Loop for country
for (country_name in names(boot_results)) {
  
  # Extract the vector of 9000 values 
  values <- boot_results[[country_name]][["bootTable"]][["value"]]
  
  # Check if the length of values is divisible by 9
  if (length(values) %% length(node_names) != 0) {
    stop(paste("Length of values for", country_name, "is not a multiple of", length(node_names)))
  }
  
  # Reshape the values into a matrix with 9 columns
  values_matrix <- matrix(values, ncol = length(node_names), byrow = TRUE)
  
  # Convert the matrix into a data frame 
  values_dataframe <- as.data.frame(values_matrix)
  colnames(values_dataframe) <- node_names
  
  # Add the country-specific data frame to the list
  boot_dataframes[[country_name]] <- values_dataframe
}
```

```{r}
# Plot for H1

# Gather centrality score in long format
long_boot_data <- do.call(rbind, lapply(names(boot_dataframes), function(country_name) {
  df <- boot_dataframes[[country_name]]
  df$country <- country_name # Add a column for the country
  return(df)
})) %>%
  melt(id.vars = "country", variable.name = "Node", value.name = "Centrality")  

# Calculate 95% bootstrapped CIs
ci_data <- long_boot_data %>%
  group_by(country, Node) %>%
  summarise(
    lower = quantile(Centrality, probs = 0.025),
    upper = quantile(Centrality, probs = 0.975),
    .groups = "drop"
  )

# Colors 
violin_colors <- ifelse(unique(long_boot_data$Node) == "INST_TR", "#008B8BB3", "#966FD6B3")

# Plot
H1b_plot = ggplot(long_boot_data, aes(x = Node, y = Centrality, fill = Node)) +
  geom_violin(alpha = 0.8) +
  geom_errorbar(data = ci_data, aes(x = Node, ymin = lower, ymax = upper), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  scale_fill_manual(values = setNames(violin_colors, unique(long_boot_data$Node))) +
  facet_wrap(~ country, scales = "free_y", ncol = 2, nrow = 4) +  
  labs(
    title = "",
    x = "Node",
    y = "Centrality"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none")

# Save
ggsave(here("Output", "H1b.jpg"), width = 10, height = 16, dpi = 300)

```

## H1c: POP is the most central node

### Estimation and network plotting

```{r}
# Network estimation and plotting

shortnames = c("rad_poison","aids_cia","elf_mindcontrol","chemtrails",
              "un_worldgov","rothschild_control","monsanto_gmo","ebola_bigpharma", "POP")

# Loop through each country
for (country_name in names(H1c_split_data)) {
  
  # Access country data
  country_matrix <- H1c_split_data[[country_name]]
  
  # Network estimation
  mgm_result <- mgm(country_matrix, type = type, level = level,
                    lambdaSel = "EBIC", ruleReg = "OR", verbose = FALSE, pbar = F)
  
  # Predictability
  pred_result <- predict(object = mgm_result, data = country_matrix, errorCon = 'R2')
  
  # Path and name
  output_path <- here("Output", "Country_networks", "H1c", paste0(country_name))
  
  # Plot with R^2 visualization
  qgraph(
    mgm_result$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = country_name, edge.color = mgm_result$pairwise$edgecolor_cb,
    vTrans = 180, borders = TRUE, vsize = 11, esize = 11, label.cex = 0.60,
    label.scale = F, filetype = "jpg", filename = output_path,
    pie = pred_result$errors[,2], # R^2 values for pies
    pieColor = rep('#FFFF00', length(shortnames)) # Yellow color for R^2 pies
  )
}
```

### Bootstrapped network estimation

```{r}
# mgm boots by country

# # Empty list 
# boot_results <- list()
# 
# # Loop for country 
# for (country_name in names(H1c_split_data)) {
# 
# # Access country data 
# country_matrix <- H1c_split_data[[country_name]]
# 
# # Bootstrapp
# boot_result <- bootnet(
#   country_matrix,
#   nBoots = 1000,
#   nCores = 8,
#   default = "mgm",
#   statistics = "strength"
# )
# 
# # Save results 
# boot_results[[country_name]] <- boot_result
# }
# 
# 
# # Save locally
# saveRDS(boot_results, here("Input", "Secondary", "boot_H1c.rds"))

# Load to save time
boot_results = readRDS(here("Input", "Secondary", "boot_H1c.rds")) 
```

### H1c plot: comparison of bootstrapped centrality scores

```{r}
# Data managment of bootstrap object

# Nodes
node_names <- c("rad_poison", "aids_cia", "elf_mindcontrol", "chemtrails",
                "un_worldgov", "rothschild_control", "monsanto_gmo", 
                "ebola_bigpharma", "POP")

# Empty list
boot_dataframes <- list()

# Loop for country
for (country_name in names(boot_results)) {
  
  # Extract the vector of 9000 values 
  values <- boot_results[[country_name]][["bootTable"]][["value"]]
  
  # Check if the length of values is divisible by 9
  if (length(values) %% length(node_names) != 0) {
    stop(paste("Length of values for", country_name, "is not a multiple of", length(node_names)))
  }
  
  # Reshape the values into a matrix with 9 columns
  values_matrix <- matrix(values, ncol = length(node_names), byrow = TRUE)
  
  # Convert the matrix into a data frame 
  values_dataframe <- as.data.frame(values_matrix)
  colnames(values_dataframe) <- node_names
  
  # Add the country-specific data frame to the list
  boot_dataframes[[country_name]] <- values_dataframe
}
```

```{r}
# Plot for H1

# Gather centrality score in long format
long_boot_data <- do.call(rbind, lapply(names(boot_dataframes), function(country_name) {
  df <- boot_dataframes[[country_name]]
  df$country <- country_name # Add a column for the country
  return(df)
})) %>%
  melt(id.vars = "country", variable.name = "Node", value.name = "Centrality")  

# Calculate 95% bootstrapped CIs
ci_data <- long_boot_data %>%
  group_by(country, Node) %>%
  summarise(
    lower = quantile(Centrality, probs = 0.025),
    upper = quantile(Centrality, probs = 0.975),
    .groups = "drop"
  )

# Colors 
violin_colors <- ifelse(unique(long_boot_data$Node) == "POP", "#008B8BB3", "#966FD6B3")

# Plot
H1c_plot = ggplot(long_boot_data, aes(x = Node, y = Centrality, fill = Node)) +
  geom_violin(alpha = 0.8) +
  geom_errorbar(data = ci_data, aes(x = Node, ymin = lower, ymax = upper), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  scale_fill_manual(values = setNames(violin_colors, unique(long_boot_data$Node))) +
  facet_wrap(~ country, scales = "free_y", ncol = 2, nrow = 4) +  
  labs(
    title = "",
    x = "Node",
    y = "Centrality"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none")

# Save
ggsave(here("Output", "H1c.jpg"), width = 10, height = 16, dpi = 300)

```

## H1d: POP is the most central node

### Estimation and network plotting

```{r}
# Network estimation and plotting

shortnames = c("rad_poison","aids_cia","elf_mindcontrol","chemtrails",
              "un_worldgov","rothschild_control","monsanto_gmo","ebola_bigpharma", "VIC")

# Loop through each country
for (country_name in names(H1d_split_data)) {
  
  # Access country data
  country_matrix <- H1d_split_data[[country_name]]
  
  # Network estimation
  mgm_result <- mgm(country_matrix, type = type, level = level,
                    lambdaSel = "EBIC", ruleReg = "OR", verbose = FALSE, pbar = F)
  
  # Predictability
  pred_result <- predict(object = mgm_result, data = country_matrix, errorCon = 'R2')
  
  # Path and name
  output_path <- here("Output", "Country_networks", "H1d", paste0(country_name))
  
  # Plot with R^2 visualization
  qgraph(
    mgm_result$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = country_name, edge.color = mgm_result$pairwise$edgecolor_cb,
    vTrans = 180, borders = TRUE, vsize = 11, esize = 11, label.cex = 0.60,
    label.scale = F, filetype = "jpg", filename = output_path,
    pie = pred_result$errors[,2], # R^2 values for pies
    pieColor = rep('#FFFF00', length(shortnames)) # Yellow color for R^2 pies
  )
}
```

### Bootstrapped network estimation

```{r}
# mgm boots by country

# # Empty list 
# boot_results <- list()
# 
# # Loop for country 
# for (country_name in names(H1d_split_data)) {
# 
# # Access country data 
# country_matrix <- H1d_split_data[[country_name]]
# 
# # Bootstrapp
# boot_result <- bootnet(
#   country_matrix,
#   nBoots = 1000,
#   nCores = 8,
#   default = "mgm",
#   statistics = "strength"
# )
# 
# # Save results 
# boot_results[[country_name]] <- boot_result
# }
# 
# 
# # Save locally
# saveRDS(boot_results, here("Input", "Secondary", "boot_H1d.rds"))

# Load to save time
boot_results = readRDS(here("Input", "Secondary", "boot_H1d.rds")) 
```

### H1d plot: comparison of bootstrapped centrality scores

```{r}
# Data managment of bootstrap object

# Nodes
node_names <- c("rad_poison", "aids_cia", "elf_mindcontrol", "chemtrails",
                "un_worldgov", "rothschild_control", "monsanto_gmo", 
                "ebola_bigpharma", "POP")

# Empty list
boot_dataframes <- list()

# Loop for country
for (country_name in names(boot_results)) {
  
  # Extract the vector of 9000 values 
  values <- boot_results[[country_name]][["bootTable"]][["value"]]
  
  # Check if the length of values is divisible by 9
  if (length(values) %% length(node_names) != 0) {
    stop(paste("Length of values for", country_name, "is not a multiple of", length(node_names)))
  }
  
  # Reshape the values into a matrix with 9 columns
  values_matrix <- matrix(values, ncol = length(node_names), byrow = TRUE)
  
  # Convert the matrix into a data frame 
  values_dataframe <- as.data.frame(values_matrix)
  colnames(values_dataframe) <- node_names
  
  # Add the country-specific data frame to the list
  boot_dataframes[[country_name]] <- values_dataframe
}
```

```{r}
# Plot for H1

# Gather centrality score in long format
long_boot_data <- do.call(rbind, lapply(names(boot_dataframes), function(country_name) {
  df <- boot_dataframes[[country_name]]
  df$country <- country_name # Add a column for the country
  return(df)
})) %>%
  melt(id.vars = "country", variable.name = "Node", value.name = "Centrality")  

# Calculate 95% bootstrapped CIs
ci_data <- long_boot_data %>%
  group_by(country, Node) %>%
  summarise(
    lower = quantile(Centrality, probs = 0.025),
    upper = quantile(Centrality, probs = 0.975),
    .groups = "drop"
  )

# Colors 
violin_colors <- ifelse(unique(long_boot_data$Node) == "POP", "#008B8BB3", "#966FD6B3")

# Plot
H1d_plot = ggplot(long_boot_data, aes(x = Node, y = Centrality, fill = Node)) +
  geom_violin(alpha = 0.8) +
  geom_errorbar(data = ci_data, aes(x = Node, ymin = lower, ymax = upper), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  scale_fill_manual(values = setNames(violin_colors, unique(long_boot_data$Node))) +
  facet_wrap(~ country, scales = "free_y", ncol = 2, nrow = 4) +  
  labs(
    title = "",
    x = "Node",
    y = "Centrality"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none")

# Save
ggsave(here("Output", "H1d.jpg"), width = 10, height = 16, dpi = 300)

```

## H2: CB index is a latent variable for mentality

```{r}
# Objects for H2
shortnames_H2 = c("government", "aliens", "technology", "elite", "drugs", "CB")

Totalgroup_comm_H2 <- list(
  "Conspiracy Mentality" = c(1:5),
  "Conspiracy Beliefs" = c(6))

Totalgroup_cols_H2 <- c("#008B8BB3", "#966FD6B3") 

#type
type_H2 = c("g","g","g","g","g","g")

#level
level_H2 = c(1,1,1,1,1,1)
```

### Estimation and network plotting

```{r}
# Network estimation and plotting

# Loop through each country
for (country_name in names(H2_split_data)) {
  
  # Access country data
  country_matrix <- H2_split_data[[country_name]]
  
  # Network estimation
  mgm_result <- mgm(country_matrix, type = type_H2, level = level_H2,
                    lambdaSel = "EBIC", ruleReg = "OR", verbose = F, pbar = F)
  
  # Predictability
  pred_result <- predict(object = mgm_result, data = country_matrix, errorCon = 'R2')
  
  # Path and name
  output_path <- here("Output", "Country_networks", "H2", paste0(country_name))
  
  # Plot with R^2 visualization
  qgraph(
    mgm_result$pairwise$wadj, layout = 'spring', labels = shortnames_H2,
    groups = Totalgroup_comm_H2, color = Totalgroup_cols_H2, legend = FALSE,
    title = country_name, edge.color = mgm_result$pairwise$edgecolor_cb,
    vTrans = 180, borders = TRUE, vsize = 11, esize = 11, label.cex = 0.60,
    label.scale = F, filetype = "jpg", filename = output_path,
    pie = pred_result$errors[,2], # R^2 values for pies
    pieColor = rep('#FFFF00', length(shortnames_H2)) # Yellow color for R^2 pies
  )
}
```

```{r}
# Define input directory for H2 and output file paths
input_directory <- here("Output", "Country_networks", "H2")
output_file <- here("Output", "H2_Net_comp.jpg")
output_file_long <- here("Output", "H2_Net_comp_long.jpg")

# Read, scale for maximum quality, and combine all JPG files in a 4x2 layout
network_images <- lapply(
  list.files(input_directory, pattern = "\\.jpg$", full.names = TRUE),
  function(file) image_scale(image_read(file), "2000x2000") # Increase image size
)

# Create a composite image in 4x2 layout
composite_image <- image_montage(
  image_join(network_images),
  tile = "4x2",
  geometry = "+20+20" # Add more spacing between images
)

# Save the 4x2 composite image
image_write(composite_image, path = output_file, format = "jpg", density = 300, quality = 100)

# Create a composite image in 2x4 layout
composite_image_long <- image_montage(
  image_join(network_images),
  tile = "2x4",
  geometry = "+20+20" # Add more spacing between images
)

# Save the 2x4 composite image
image_write(composite_image_long, path = output_file_long, format = "jpg", density = 300, quality = 100)
```


### Bootstrapped network estimation

```{r}
# mgm boots by country
 
# # Empty list for bootstrapped results
# boot_result_H2 <- list()
# 
# # Loop for each country
# for (country_name in names(H2_split_data)) {
#   
#   # Access country data
#   country_matrix <- H2_split_data[[country_name]]
#   
#   # Bootstrapping
#   boot_result <- bootnet(
#     country_matrix,
#     nBoots = 1000,
#     nCores = 8,
#     default = "mgm",
#     statistics = "strength"
#   )
#   
#   # Save results in the list
#   boot_result_H2[[country_name]] <- boot_result
# }
# 
# # Save locally
# saveRDS(boot_result_H2, here("Input", "Secondary", "boot_H2.rds"))

# To save time, load bootstrapped results
boot_result_H2 <- readRDS(here("Input", "Secondary", "boot_H2.rds"))
```

### H2 plot

```{r}
# Data managment of bootstrap object

# Nodes
node_names <- c("government", "aliens", "technology", "elite", "drugs", "CB")

# Empty list
boot_dataframes <- list()

# Loop for each country
for (country_name in names(boot_result_H2)) {
  
  # Extract the vector of bootstrap values
  values <- boot_result_H2[[country_name]][["bootTable"]][["value"]]
  
  # Check if the length of values is divisible by the number of nodes
  if (length(values) %% length(node_names) != 0) {
    stop(paste("Length of values for", country_name, "is not a multiple of", length(node_names)))
  }
  
  # Reshape the values into a matrix with 6 columns (one for each node)
  values_matrix <- matrix(values, ncol = length(node_names), byrow = TRUE)
  
  # Convert the matrix into a data frame
  values_dataframe <- as.data.frame(values_matrix)
  colnames(values_dataframe) <- node_names
  
  # Add the country-specific data frame to the list
  boot_dataframes[[country_name]] <- values_dataframe
}
```

```{r}
# Plot for H2

# Gather centrality scores in long format
long_boot_data <- do.call(rbind, lapply(names(boot_dataframes), function(country_name) {
  df <- boot_dataframes[[country_name]]
  df$country <- country_name # Add a column for the country
  return(df)
})) %>%
  melt(id.vars = "country", variable.name = "Node", value.name = "Centrality")

# Calculate 95% bootstrapped CIs
ci_data <- long_boot_data %>%
  group_by(country, Node) %>%
  summarise(
    lower = quantile(Centrality, probs = 0.025),
    upper = quantile(Centrality, probs = 0.975),
    .groups = "drop"
  )

# Colors
violin_colors <- ifelse(unique(long_boot_data$Node) == "CB", "#966FD6B3","#008B8BB3")

# Plot
H2 <- ggplot(long_boot_data, aes(x = Node, y = Centrality, fill = Node)) +
  geom_violin(alpha = 0.8) +
  geom_errorbar(data = ci_data, aes(x = Node, ymin = lower, ymax = upper), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  scale_fill_manual(values = setNames(violin_colors, unique(long_boot_data$Node))) +
  facet_wrap(~ country, scales = "free_y", ncol = 2, nrow = 4) +  
  labs(
    title = "",
    x = "Node",
    y = "Centrality"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )

# Save
ggsave(here("Output", "H2.jpg"), H2, width = 10, height = 16, dpi = 300)

```

## Figure_1

```{r}
# Define the input file paths
file_H1 <- here("Output", "Country_networks", "H1", "USA.jpg")
file_H2 <- here("Output", "Country_networks", "H2", "USA.jpg")

# Define output file paths
output_file_wide <- here("Output", "Figure_1_Wide.jpg")
output_file_long <- here("Output", "Figure_1_Long.jpg")

# Read and scale the two images
network_images <- lapply(
  c(file_H1, file_H2),
  function(file) image_scale(image_read(file), "2000x2000") # Increase image size
)

# Create a wide  image 
composite_image_wide <- image_append(image_join(network_images), stack = FALSE)

# Save 
image_write(composite_image_wide, path = output_file_wide, format = "jpg", density = 300, quality = 100)

# Create a long image 
composite_image_long <- image_append(image_join(network_images), stack = TRUE)

# Save
image_write(composite_image_long, path = output_file_long, format = "jpg", density = 300, quality = 100)
```


## All data

```{r}
# objects for network 
shortnames = c("POP", "INST_TR", "VIC", "CM", "CB")

# Country color palette 
country_colors <- c(
  "DEU" = "#E41A1C", "ESP" = "#377EB8", "FRA" = "#4DAF4A", 
  "GBR" = "#984EA3", "ITA" = "#FF7F00", "POL" = "#ffcf33",
  "SWE" = "#A65628", "USA" = "#008080")

Totalgroup_comm <- list(
  "Determinants" = c(1:4),
  "Conspiracy Beliefs" = c(5))

Totalgroup_cols <- c("#966FD6B3", "#008B8BB3") 

#type
type = c("g","g","g","g","g")

#level
level = c(1,1,1,1,1)

```


```{r}
# Network estimation and plotting

# Loop through each country
for (country_name in names(all_data_split_data)) {
  
  # Access country data
  country_matrix <- all_data_split_data[[country_name]]
  
  # Network estimation
  mgm_result <- mgm(country_matrix, type = type, level = level,
                    lambdaSel = "EBIC", ruleReg = "OR", verbose = FALSE, pbar = F)
  
  # Predictability
  pred_result <- predict(object = mgm_result, data = country_matrix, errorCon = 'R2')
  
  # Path and name
  output_path <- here("Output", "Country_networks", "all_data", paste0(country_name))
  
  # Plot with R^2 visualization
  qgraph(
    mgm_result$pairwise$wadj, layout = 'spring', labels = shortnames,
    groups = Totalgroup_comm, color = Totalgroup_cols, legend = FALSE,
    title = country_name, edge.color = mgm_result$pairwise$edgecolor_cb,
    vTrans = 180, borders = TRUE, vsize = 11, esize = 11, label.cex = 0.60,
    label.scale = F, filetype = "jpg", filename = output_path,
    pie = pred_result$errors[,2], # R^2 values for pies
    pieColor = rep('#FFFF00', length(shortnames)) # Yellow color for R^2 pies
  )
}
```


